\documentclass[12pt]{article} %scrartcl


% bibliographie
\usepackage[round, authoryear]{natbib}

%accents, language français
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[french]{babel} %
\usepackage{csquotes}
%\usepackage{xltxtra}

%Lien
\usepackage[colorlinks=true,urlcolor=blue, citecolor=black]{hyperref}

%Image
\usepackage[pdftex]{graphicx}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} %Pour la page de titre

% Font

% Outline numbering
\setcounter{secnumdepth}{0}
% Set interligne
\linespread{1.5}
% Page layout (geometry)
\usepackage[a4paper]{geometry}
\geometry{left=2.4cm,right=2cm,top=2cm,bottom=2cm}
% Pages styles
\pagestyle{plain}


\begin{document}

\section{Probes}
\label{sec:probes}

Is it relevant to want to test community differences in soil moisture ?

I think that not because of those reasons:

\begin{itemize}
	\item Saplings will be not enough big (root system), they will be in transplant shock.
	\item The variability between the terrace and between nurse will be probably higher than community effects.
		
\end{itemize}

For Arturo, he would have anyway the functional strategies and the functional traits arguments to justify his results (based on his own predictions).

\subsubsection{Practical points}
\label{ssub:}

\begin{itemize}
	\item How to design the probes location ?
	\item Show to Arturo how I put the first probes.
\end{itemize}

\section{Arturo internship}
\label{sec:arturo_internship}

\begin{itemize}
	\item Establishment of planning with Arturo in order to find the better trade-off between his availabilities and his project.
	\item Finish to enter my data and send them to Arturo.
	\item Set up a shared dropbox folder for his project.
	
\end{itemize}

\section{Watering treatment}
\label{sec:}

\begin{itemize}
	\item January:
		\begin{itemize}
			\item Choose the complete communities that I will have
			\item Color in red with a paint bomb the holes chosen for the watering treatment.
		\end{itemize}

	\item February:
		\begin{itemize}
			\item Watering ? To maximize the differences between the treatments in march (functional traits). If we do, I have to find someone to water in February.
		\end{itemize}
		
\end{itemize}

\section{Functional traits}
\label{sec:functional_traits}

\begin{itemize}
	\item Which are the lab for sending the leaves for analysis ? What is the price ?
	\item Order the material in January (the next session in Alicante).
\end{itemize}

\section{Phenology internship}
\label{sec:}

\begin{itemize}
	\item How much time is during a master internship ? When is the starting ?
	\item What are the expense I have to plan for those internship ?
	\item What are the requirements of the master degree internship in Spain ?
\end{itemize}



\section{Student card}
\label{sec:student_card}

\begin{itemize}
	\item Where can I begin the process of doing my student card ?
\end{itemize}

\end{document}
