---
title: "Analysis document - first paper"
output:
  pdf_document:
    highlight: zenburn
    fig_width: 4
    fig_height: 4
    fig_caption: true
    toc: true
    toc_depth: 3
    number_sections: true
  geometry: margin=2cm
  word_document:
    highlight: zenburn
    fig_width: 4
    fig_height: 4
    fig_caption: true
    toc: true
---

```{r load_library, echo = FALSE}
library(fields)
library(clue)
library(lubridate)
library(tidyverse)
library(broom)
library(stringr)
library(cowplot)
library(survival)
library(lme4)
library(GGally)
library(xtable)
library(survival)
```

```{r graph_conf, echo = FALSE}

surv_graph_conf <-  labs(x = "# month since the starting of the experiment", y = "Proportion of survival")
n_index_graph_conf <-  labs(x = "Number of month since the starting of the experiment", y = "Interaction index (NIntA)")

dodge <- position_dodge(width=0.9)
font_size = 8 
letter_size = 3
theme_set(theme_cowplot(font_size=font_size))
conf <- theme(
    plot.margin = unit(c(6,0,6,0), "pt"),
    #axis.text.x = element_text(face="italic"),
    #axis.title.x = element_blank(),
    legend.position="none" 
    )

p_stars <- function(x){
    stopifnot(is.numeric(x), is.vector(x))
   star <- vector("character", length(x))
   star[round(x, 2) >= 0.05] <- "n.s." 
   star[round(x, 2) == 0.05] <- "." 
   star[round(x, 3) < 0.05] <- "*"
   star[round(x, 3) < 0.01] <- "**"
   star[round(x, 4) < 0.001] <- "***"
   return(star)
}

```

- TODO:
  - The three graphs: (gradient C-S, dist to optimum, diversity effect)

## Material & Methods

```{r load_data, echo = FALSE}

data_0 <- read_csv2("./data-raw/biomass_t0.csv") %>%
    select(species, ind, height, dia1, dia2) %>%
    mutate(
	species = str_to_lower(species),
	d = rowMeans(cbind(dia1, dia2), na.rm = TRUE)) %>%
    select(-dia1, -dia2)

summary_sp_0 <- data_0 %>%
    gather(key = variable, value = value, height, d) %>%
    mutate(variable = str_replace_all(variable, c("height" = "h0",  "d" = "d0"))) %>%
    group_by(species, variable) %>%
    summarise(
	mean = mean(value, na.rm = TRUE),
	sd = sd(value, na.rm = TRUE)
	) 
mean_sp_0 <- summary_sp_0 %>%
    select(-sd) %>%
    spread(variable, mean)

data(holes_data)

```

```{r data simulation, echo = FALSE, eval = FALSE}
## Simulate data from t0 

## simulate the same number of data that in january 
n_jan <- filter(holes_data, date == "janv. 2016") %>%
    group_by(species) %>%
    summarise(n= n()) 

## Simulation
simul_t0 <- inner_join(summary_sp_0, n_jan) %>%
    mutate(simul = pmap(list(n, mean, sd), 
	    function(n, mean, sd) rnorm(n = n, mean = mean, sd = sd))) %>%
    ungroup() %>%
    select(-n, -mean, -sd) %>%
    unnest() %>% 
    mutate(date = "nov. 2015") #%>%
#    spread(key = variable, value = simul)

```

```{r rgr_computation, echo = FALSE}
###############################################################################
# RGR data  building

## first method
holes_data2 <- inner_join(holes_data, mean_sp_0) %>%
    mutate(ln_d = log(d) - log(d0),
	ln_h = log(h) - log(h0), 
	ln_hm = log(hm) - log(h0),
	duration = yearmon2month(date),
	rgr_d = ln_d/duration,
	rgr_h = ln_h/duration,
	rgr_hm = ln_hm/duration
	)

rgr_data <- select(holes_data2, -ln_d, -ln_h, -ln_hm, -duration, -d0, -h0, -hm , -h, -d) %>%
ungroup() %>%
mutate(date_m = month(date),
duration_m = date_m + 2)

rgr_t0 <- filter(rgr_data, date != "nov. 2016", surv != 0) %>%
ungroup() %>%
mutate(date_m = month(date),
duration = date_m + 2,
rgr_d1 = rgr_d + 1)

## Second method
rgr2 <- group_by(holes_data, label, species) %>% 
    mutate(ln_d = c(NA,diff(log(d))),
ln_h = c(NA,diff(log(h))), 
ln_hm = c(NA,diff(log(hm))),
duration = yearmon2month(date),
duration = as.integer(duration + 1),
rgr_d = ln_d/duration,
rgr_h = ln_h/duration,
rgr_hm = ln_hm/duration 
) %>% 
filter(surv != 0)#date != "nov. 2016", 

rgr2_summary <- gather(rgr2, key = "variable", value = "value", rgr_d,
    rgr_h, rgr_hm) %>%
    group_by(duration, species, com, ms, watering, variable) %>%
    summarise(
	mean = mean(value, na.rm = TRUE),
	ic_width = 1.96*sd(value, na.rm = TRUE)/sqrt(n())
      	)

# ind data surv 
load("./data/try2.RData")
try2_ok <- try2 %>%
    mutate(date_m = month(date), duration_m = date_m + 2) %>%
    mutate(
	surv = ifelse(survival == 0, TRUE, FALSE),
	com = ifelse(com %in% c("A", "D", "P"), "Mono", "Poly"),
	ms = ifelse(ms == "0", "Open", "Patch"),
	watering = ifelse(watering == "0", "No Watered", "Watered"),
	watering = as.factor(watering),
	species = as.factor(species)
	)
# Holes data surv
holes_data_surv <- holes_data2  %>%
    mutate(date_m = month(date), duration_m = date_m + 2)

# Holes data surv summary
holes_data_surv_summary <- holes_data2  %>%
    mutate(date_m = month(date),
	duration_m = date_m + 2) %>%
    group_by(duration_m, ms, com, watering, species) %>%
    summarise(
	mean = mean(surv, na.rm = T),
	ic_width = 1.96*sd(surv, na.rm = T)/sqrt(n())
	)

```

## Data selection

### RGR max

```{r pre_rgr_boxplot, echo = FALSE}
p <- ggplot(rgr2, 
    aes(x = as.factor(date), y = rgr_d)) + 
    geom_boxplot(aes(linetype = watering, colour = ms)) +
    ylab("RGR of basal diameter") 
p + facet_grid(com ~ species)

```
```{r pre_rgr_plotmeans, echo = FALSE}
p <- ggplot(filter(rgr2_summary, variable == "rgr_d"), 
    aes(x = duration, y = mean, colour = ms, linetype = watering)) + 
    geom_line() + geom_point() +
    geom_errorbar(aes(ymin = mean - ic_width, ymax = mean + ic_width), width = 0.025)
p + facet_grid(com ~ species)
```
```{r data_mars, echo = FALSE}
rgr2_march  <- filter(rgr2, date == "mars 2016") %>%
    select(ter, plot, label,  ms, com, watering, species, rgr_d, duration) %>%
    mutate(rgr_d1 = rgr_d +1)
```

## Analysis

### Gradient CS

```{r gradient_CS_plot, echo = FALSE}
p <- ggplot(filter(holes_data_surv_summary, ms == "Open", watering
	== "No Watered"), 
    aes(x = duration_m, y = mean, colour = species)) + 
    geom_line() + geom_point() +
    geom_errorbar(aes(ymin = mean - ic_width, ymax = mean + ic_width), width = 0.025) +
    labs(colour = "") + # Remove legend title
    theme(legend.position = "bottom") 

p + facet_grid(com ~.)

legend <- get_legend(p)
legend_b <- get_legend(p + theme(legend.position = "bottom"))
legend_t <- get_legend(p + theme(legend.position = "top"))

g1 <- p + facet_grid(com ~.) + 
    surv_graph_conf +
    conf
g2 <- plot_grid(
    g1, 
    legend_b, 
    nrow = 2,
    rel_heights = c(9, 1)
    )


save_plot(filename = "cs_gradient.pdf",
    plot = g2,
    base_height = 71,
    base_width = 71, # make room for figure legend
    path = "~/Documents/thesis/papers/spain_diversity/figures",
    unit = "mm"
    )

```
```{r gradient_CS_table, echo = FALSE}

holes_data_surv_summary_open <- filter(holes_data_surv_summary, ms == "Open")%>% 
    ungroup() %>%
    select(-ms) %>%
    mutate(duration_m = as.factor(duration_m))

surv_table_ok <- xtable(holes_data_surv_summary_open)
label(surv_table_ok) <- c("tab:surv")
digits(surv_table_ok) <- c(1,1,1,1,1, 2, 2)
caption(surv_table_ok) <- paste("Proportion of survival summary according to
    the duration of the experiment and the variable manipulated.", sep="")

print(surv_table_ok, include.rownames = FALSE,
    file = "~/Documents/thesis/papers/spain_diversity/surv_table.tex")

```

# Results

## ANOVA

```{r anova, echo = FALSE}

anova_data <- filter(rgr_t0, duration == 5)

## LMER
test <- lmer(rgr_d ~ ms + watering + com + species + (1 | plot), anova_data)
test2 <- lmer(rgr_d ~ ms*species + watering + com + species + (1 | plot), anova_data)
test3 <- lmer(rgr_d ~ ms*species + watering*species + com + (1 | plot), anova_data)
test4 <- lmer(rgr_d ~ ms*species + watering*species + com*species + (1 | plot), anova_data)
test5 <- lmer(rgr_d ~ ms*species*watering*com + (1 | plot), anova_data)

anova(test, test2, test3, test4, test5)
summary(test5)

## LM
test <- lm(rgr_d ~ ms + watering + com + species , anova_data)
test2 <- lm(rgr_d ~ ms*species + watering + com + species , anova_data)
test3 <- lm(rgr_d ~ ms*species + watering*species + com , anova_data)
test4 <- lm(rgr_d ~ ms*species + watering*species + com*species , anova_data)
test5 <- lm(rgr_d ~ ms*species*watering*com , anova_data)

anova(test, test2, test3, test4, test5)
summary(test5)

anova_table <- anova(test5) 
anova_table2 <- tidy(anova_table) %>%
    mutate(stars = p_stars(p.value)) %>%
 arrange(desc(statistic)) %>%
    rename(Factor = term, DF = df, SS = sumsq, MS = meansq, "F-values"
	= statistic, "P-values" = p.value, "sig. lvl" = stars)
    
anova_table3 <- glance(anova_table)

anova_table_ok <- xtable(anova_table2)
label(anova_table_ok) <- c("tab:anova")
digits(anova_table_ok) <- c(1, 1,1, 4, 4, 2, 4, 1)
ajusted_r_squared <- round(summary(test5)$adj.r.squared, 2)
caption(anova_table_ok) <- paste("ANOVA summary of the complete model from the
    experiment (all the manipulated variable and the interactions between them)
    considering the basal diameter RGR of march. The adjusted R squared is $",
    ajusted_r_squared, "$. DF: Degree of freedom, SS: Sum of Squares, MS: Means
    of Squares, *: \\textit{P} < 0.05, **: \\textit{P} < 0.01 and ***:
    \\textit{P} < 0.001. species: identity of the sapling (Anthyllis cytisoides,
	Dorycnium pentaphyllum or Pistachia lentiscus), com: diversity of the
    sapling community composition (monospecific or multispecies community),
    watering: intermittent water supplementation (yes of no), ms: microsite
    (open or patch).", sep="")

print(anova_table_ok, include.rownames = FALSE,
    file = "~/Documents/thesis/papers/spain_diversity/anova_table.tex")

```
```{r pseudo_pairs, echo = FALSE, eval = TRUE}
load("../../data/processed/try2.RData")
holes_pairs <- filter(try2, date == "janv. 2016", ind == "1") %>%
    select(ter, label, ms, com, watering) %>%
    group_by(ter, com, watering) %>%
    arrange(label) %>%
    nest()

##dataset to choose:
# - rgr2 or rgr2_march: d or rgr(t) = (ln(X_t) - ln(X_{t-1}))/(T_t - T_{t-1})
# - rgr_t0: rgr(t) = (ln(X_t) - ln(X_{t-1}))/(T_t - T_0)
dataset_ok <- rgr_t0
## Choose response variable
var_rep <- "rgr_d1"
## Choose explicative variable
var_exp <- c("label", "species", "ms", "com", "watering", "duration")


# Make the pairs
holes_pairs2 <- holes_pairs %>%
    mutate(pair = map(data, pair_find)) %>%
    unnest(pair) %>%
    mutate(
	pair_id = as.numeric(rownames(.)),
	Patch = as.integer(Patch),
	Open = as.integer(Open)
	)

# Make open and patch dataset
test <- select_(dataset_ok, .dots = c(var_rep, var_exp))

## Open dataset
test_open <- filter(test, ms == "Open", label %in% holes_pairs2$Open) %>%
    left_join(., select(holes_pairs2, Open, pair_id) %>% rename(label = Open)) %>% 
    arrange(pair_id) %>%
    ungroup() %>%
    select(-ms, - label) %>% rename_(Open = var_rep)
## Patch dataset    
test_patch <- filter(test, ms == "Patch", label %in% holes_pairs2$Patch) %>%
    left_join(., select(holes_pairs2, Patch, pair_id) %>% rename(label =
	    Patch)) %>%
    arrange(pair_id) %>%
    ungroup() %>%
    select(-ms, - label) %>% rename_(Patch = var_rep)
## Join dataset
paired_data <- left_join(test_open, test_patch)
paired_index <- paired_data %>%
    mutate(n_int_a = map2_dbl(Open, Patch, n_int_a)) %>%
    select(-Open, -Patch)

paired_index_summary <- paired_index %>%
    group_by(duration, species, com, watering) %>%
    summarise(
	mean = mean(n_int_a, na.rm = TRUE),
	sd = sd(n_int_a, na.rm = TRUE),
	ic_width = 1.96*sd/sqrt(n())
      	)

```

## Survival analysis

```{r survival, echo = FALSE}
holes_data_surv2  <- filter(holes_data_surv, ms == "Open") %>% ungroup() %>%
    mutate(species = as.factor(species))
try_data_surv  <- filter(try2_ok, ms == "Open")
test <- survfit(Surv(holes_data_surv2$duration_m, surv) ~ species + com +
    watering, holes_data_surv2) 
plot(test)
str(test)

lm_surv <- survdiff(Surv(holes_data_surv2$duration_m, surv) ~ com + ms +
    watering, holes_data_surv2, rho=0)
summary(lm_surv)

my.surv <- Surv(try2_ok$duration_m, try2_ok$surv)
my.fit <- summary(survfit(my.surv ~ 1))
coxph.fit <- coxph(my.surv ~ species * com * watering, data = try2_ok,
    method="breslow")
coxph.fit
anova(coxph.fit)


test <- summary(coxph.fit)
ajusted_r_squared <- round(test$rsq[1], 2)
test2 <- test$coefficients
term <- dimnames(test2)[[1]]
term
term2 <- c("dorycnium", "pistachia", "com", "watering", "dorycnium:com",
    "pistachia:com", "dorycnium:watering", "pistachia:watering", "com:watering",
    "dorycnium:com:watering", "pistachia:com:watering")

test3 <- as_tibble(test2) %>% 
    mutate(Factor = term2) %>%
select(Factor, coef, `exp(coef)`, `se(coef)`, z, `Pr(>|z|)`) %>%
    rename(`$\\beta$` = coef, `$e^\\beta$` =`exp(coef)`, SE = `se(coef)`,
	`Z-values` = z, `P-values` = `Pr(>|z|)`)

cox_table_ok <- xtable(test3)
label(cox_table_ok) <- c("tab:cox")
digits(cox_table_ok) <- c(1, 1, 2, 2, 2, 3, 4)
caption(cox_table_ok) <- paste("Summary of the Cox proportional hazards. The adjusted R squared equaled to $", ajusted_r_squared, "$.",
    sep="")

print(cox_table_ok, include.rownames = FALSE, sanitize.colnames.function =
    identity, file = "~/Documents/thesis/papers/spain_diversity/cox_table.tex")

```

## Dist to optimum

```{r plot_duration, echo = FALSE}
p <- ggplot(filter(paired_index_summary, com == "Mono", duration == 5), 
    aes(x = species, y = mean)) + 
    geom_point() +
    ylab("Interaction index (NIntA)") +
    geom_errorbar(aes(ymin = mean - ic_width, ymax = mean + ic_width), width = 0.025)
p + facet_grid(. ~ watering)

```
```{r plot_duration2, echo = FALSE}
p <- ggplot(filter(paired_index, duration == 5), 
    aes(x = species, y = n_int_a)) + 
    geom_boxplot() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")
p + facet_grid(com ~ watering)

```
```{r dist_opt_cor, echo = FALSE}
dist2opt_temp <- filter(paired_index, duration == 5) 
dist2opt_table <- group_by(dist2opt_temp, com, watering) %>%
    mutate(rank_sp = as.numeric(as.factor(species))) %>%
    summarise(
	spearman = cor( x = rank_sp, y = n_int_a, method = "spearman",
	   use = "pairwise.complete.obs"),
       spearman.p = cor.test( x = rank_sp, y = n_int_a, method = "spearman",
	   use = "pairwise.complete.obs", alternative = "greater", exact = FALSE)$p.value
       )

#map2_dbl(rank_sp, n_int_a, cor, method = "spearman")
test_table <-  mutate(dist2opt_table,
    species = "dorycnium",
    n_int_a = 0.4,
    spearman = round(spearman, 3),
    spearman.p = round(spearman.p, 4)
    )

g1 <- p + facet_grid(com ~ watering) + 
    geom_text(data = test_table, 
	aes(label = paste("Spearman~~", "rho==", spearman, "~~P==", spearman.p,
		sep = "")), #, " = ", spearman, ", P = ", spearman.p
	size = letter_size -1,
	parse = TRUE # Important to display math
	)

#save_plot(filename = "dist_optimum.pdf",
    #plot = g1,
    #base_height = 100,
    #base_width = 140, # make room for figure legend
    #path = "~/Documents/thesis/papers/spain_diversity/figures",
    #unit = "mm"
    #)

```

## Diversity effect

```{r div_effect_plot_sp, echo = FALSE}
p <- ggplot(filter(paired_index, duration == 5), 
    aes(x = species, y = n_int_a, color= com)) + 
    geom_boxplot() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")
p + facet_grid(. ~ watering)

```
```{r div_effect_test, echo = FALSE}
div_effect_temp <- filter(paired_index, duration == 5) 
div_effect_table <- group_by(div_effect_temp, species, watering) %>%
    spread(com, value = n_int_a) %>%
    do(tidy(wilcox.test(.$Mono, .$Poly, na.rm= TRUE)) 
       ) %>%
    mutate(n_int_a = 0.4, com = "Poly",
	stars = p_stars(p.value),
	p.value = round(p.value, 3))

```
```{r div_effect_plot_sp, echo = FALSE}
g1 <- p + facet_grid(. ~ watering) +
    geom_text(data = div_effect_table, 
	aes(label = paste(stars,
		sep = "")), 
	size = letter_size -1,
	parse = FALSE # Important to display math
	) + 
    theme(axis.text.x = element_text(angle=-45, hjust=0))
g1

```

Idea: put a forth panel with the boxplot containing all the data and the t-test

```{r div_effect_test_tot, echo = FALSE}
div_effect_table_tot <- group_by(div_effect_temp) %>%
    spread(com, value = n_int_a) %>%
    do(tidy(wilcox.test(.$Mono, .$Poly, na.rm= TRUE)) 
       )%>%
    mutate(n_int_a = 0.4, com = 1.5,
	p.value = round(p.value, 3))
```

```{r div_effect_plot_tot, echo = FALSE}
p <- ggplot(filter(paired_index, duration == 5), 
    aes(x = com, y = n_int_a)) + 
    geom_boxplot() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")

g2 <- p + geom_text(data = div_effect_table_tot, 
	aes(label = paste("Wilcoxon~~", "W==", statistic, "~~P==", p.value,
		sep = "")), #, " = ", spearman, ", P = ", spearman.p
	size = letter_size -1,
	parse = TRUE # Important to display math
	)

```

```{r div_effect_plot_gather, echo = FALSE}
g3 <- plot_grid(g1, g2, labels = "auto", align = 'h', rel_widths =
    c(1, 0.5))

#save_plot(filename = "div_effect.pdf",
    #plot = g3,
    #base_height = 71,
    #base_width = 140, # make room for figure legend
    #path = "~/Documents/thesis/papers/spain_diversity/figures",
    #unit = "mm"
    #)

```

## Dominance effect  

Test if in poly there is a negative correlation of NIntA between species 

```{r div_dominance_correlation, echo = FALSE}
dominance_data <- filter(paired_index, com == "Poly", duration == 5) %>% 
spread(species, value = n_int_a) 

ggpairs(select(dominance_data, watering, anthyllis:pistachia), ggplot2::aes(colour =
	watering))

cor(select(dominance_data, anthyllis:pistachia), use = "pairwise.complete.obs")
```
We have negative correlations between Anthyllis and Pistachia in watered,
between Dorycnium and Anthyllis in no watered treatment, and a positive
correlation between Pistachia and Dorycnium in the watered treatment.

Let's check the ranking of the species (rgr_d) in each treatment to check if
there are patterns helping to make the difference between micro-environment and
dominance.  (correlation between rank rgr_d in poly)

```{r rank_species_d, echo = FALSE}
rank_sp <- filter(paired_data, com == "Poly", duration == 5) %>%
    group_by(pair_id) %>%
    mutate(
	open_rank = rank(Open),
	patch_rank = rank(Patch)
	)
temp <- filter(paired_index, com == "Poly", duration == 5) %>%
    group_by(pair_id) %>%
    mutate(int_rank = rank(n_int_a))
rank_sp2 <- left_join(rank_sp, temp); rm(temp)

rank_sp2 %>%
    gather(variable, value, Open, Patch, n_int_a)

cor(filter(rank_sp2, watering == "No Watered") %>%
    select(open_rank, patch_rank, int_rank), 
    use = "pairwise.complete.obs")

ggpairs(select(rank_sp2, open_rank, patch_rank, int_rank, species, watering), ggplot2::aes(colour =
	species, shape = watering))

```

## Competition more intense in open ?

```{r test_compet_div, echo = FALSE}
rgr2_march

p <- ggplot(filter(rgr2_march, ms == "Open"), 
    aes(x = species, y = rgr_d, color= com)) + 
    geom_boxplot() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")
p + facet_grid(. ~ watering)


p <- ggplot(filter(rgr2_march, ms == "Patch"), 
    aes(x = species, y = rgr_d, color= com)) + 
    geom_boxplot() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")
p + facet_grid(. ~ watering)

p <- ggplot(rgr2_march, 
    aes(x = species, y = rgr_d, color= com)) + 
    geom_boxplot() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")
p + facet_grid(ms ~ watering)
```


# Appendices 

```{r allometry_assessment, echo = FALSE}
data <- read.table("../data/biomass_t0.csv", sep=";", dec=",", header=T)

data[, "biomass"] <- data[, "bio_stem"] + data[, "bio_roots"] + data[, "bio_leaves"]
data[, "diameter"] <- ( data[, "dia1"] + data[, "dia2"] )/2

variable <- c("diameter")        #Explicative variables
# , "Vegetative height (cm)"

par(pch=20, mfrow=c(1,2))
pdf(file = "~/Documents/thesis/papers/spain_diversity/figures/allometry.pdf", width = 6, height = 6)
for (i in 1:length(variable)) {
	plot( data[data$species=="Dorycnium", "biomass"] ~ data[data$species=="Dorycnium", variable[i]],
		xlab="Basal diameter (mm)", ylab="Total biomass (g)",
		ylim=range(data$biomass), xlim=range(data[,variable[i]])
		)
	points(data[data$species=="Anthyllis", "biomass"] ~ data[data$species=="Anthyllis", variable[i]], col="red")
	points(data[data$species=="Pistacia", "biomass"] ~ data[data$species=="Pistacia", variable[i]], col="green")
	abline(lm(data[data$species=="Anthyllis", "biomass"] ~ data[data$species=="Anthyllis", variable[i]] ), col="red")
	abline(lm(data[data$species=="Dorycnium", "biomass"] ~ data[data$species=="Dorycnium", variable[i]] ), col="black")
	abline(lm(data[data$species=="Pistacia", "biomass"] ~ data[data$species=="Pistacia", variable[i]] ), col="green")

}
dev.off()

mod <- lm(biomass ~ diameter + diameter:species , data)
mod <- lm(biomass ~ diameter*species , data)
summary(mod)

```

## Number of holes available

Number of holes in which there is still at least one sapling alive 

```{r holes_alive_time, echo = FALSE, fig.width=8, fig.height=4}
n_data_date <- holes_data %>%
    mutate(date_m = month(date),
    duration_m = date_m + 2) %>%
    group_by(duration_m, species, ms, com, watering) %>%
    filter(surv != 0) %>%
    summarise(n_count = n())

g <- ggplot(n_data_date, 
    aes(y = n_count, x = duration_m, fill = species, colour = ms, alpha = com)) +  
    geom_bar(stat="identity", position = "dodge")+
    labs(x = "Number of months since the beginning of the experiment", y =
	"Count")
g + facet_grid(. ~ watering)

save_plot(filename = "nb_holes_alive.pdf",
    plot = g,
    base_height = 71,
    base_width = 140, # make room for figure legend
    path = "~/Documents/thesis/papers/spain_diversity/figures",
    unit = "mm"
    )
```

## RGR time series

```{r rgr_time_series, echo = FALSE}
rgr_summary <- gather(rgr_t0, key = "variable", value = "value", rgr_d,
    rgr_h, rgr_hm) %>%
    group_by(duration_m, species, com, ms, watering, variable) %>%
    summarise(
	mean = mean(value, na.rm = TRUE),
	ic_width = 1.96*sd(value, na.rm = TRUE)/sqrt(n())
      	)

p <- ggplot(filter(rgr_summary, variable == "rgr_d"), 
    aes(x = duration_m, y = mean, colour = ms, linetype = watering)) + 
labs(x = "Number of months since the beginning of the experiment", y = "Basal
    diameter RGR (mm.month^-1)") +
    geom_line() + geom_point() +
    geom_errorbar(aes(ymin = mean - ic_width, ymax = mean + ic_width), width = 0.025)
p2 <- p + facet_grid(com ~ species)
p2

save_plot(filename = "rgr_d_data_series.pdf",
    plot = p2,
    base_height = 100,
    base_width = 160, # make room for figure legend
    path = "~/Documents/thesis/papers/spain_diversity/figures",
    unit = "mm"
    )

```

