---
title: "Analysis document - first paper"
output:
  pdf_document:
    highlight: zenburn
    fig_width: 4
    fig_height: 4
    fig_caption: true
    toc: true
    number_sections: true
  geometry: margin=2cm
  word_document:
    highlight: zenburn
    fig_width: 4
    fig_height: 4
    fig_caption: true
    toc: true
---

```{r load_library, echo = FALSE}
devtools::load_all()
library(fields)
library(clue)
library(lubridate)
library(tidyverse)
library(broom)
library(stringr)
library(cowplot)
library(survival)
library(lme4)
library(GGally)
library(xtable)
library(survival)
```

```{r graph_conf, echo = FALSE}

surv_graph_conf <-  labs(x = "# month since the starting of the experiment", y = "Proportion of survival")
n_index_graph_conf <-  labs(x = "Number of month since the starting of the experiment", y = "Interaction index (NIntA)")

dodge <- position_dodge(width=0.9)
font_size = 8
letter_size = 3
theme_set(theme_cowplot(font_size=font_size))
conf <- theme(
    plot.margin = unit(c(6,0,6,0), "pt"),
    #axis.text.x = element_text(face="italic"),
    #axis.title.x = element_blank(),
    legend.position="none"
    )

p_stars <- function(x){
    stopifnot(is.numeric(x), is.vector(x))
   star <- vector("character", length(x))
   star[round(x, 2) >= 0.05] <- "n.s."
   star[round(x, 2) == 0.05] <- "."
   star[round(x, 3) < 0.05] <- "*"
   star[round(x, 3) < 0.01] <- "**"
   star[round(x, 4) < 0.001] <- "***"
   return(star)
}

```

- TODO:
  - The three graphs: (gradient C-S, dist to optimum, diversity effect)

## Material & Methods

```{r load_data, echo = FALSE}

data_0 <- read_csv2(here::here("data-raw/biomass_t0.csv")) %>%
    select(species, ind, height, dia1, dia2) %>%
    mutate(
	species = str_to_lower(species),
	d = rowMeans(cbind(dia1, dia2), na.rm = TRUE)) %>%
    select(-dia1, -dia2) %>%
    mutate(species = str_replace_all(species, "pistacia", "pistachia") )

summary_sp_0 <- data_0 %>%
    gather(key = variable, value = value, height, d) %>%
    mutate(variable = str_replace_all(variable, c("height" = "h0",  "d" = "d0"))) %>%
    group_by(species, variable) %>%
    summarise(
	mean = mean(value, na.rm = TRUE),
	sd = sd(value, na.rm = TRUE)
	)
mean_sp_0 <- summary_sp_0 %>%
    select(-sd) %>%
    spread(variable, mean)
data(holes_data)

```
```{r data simulation, echo = FALSE, eval = FALSE}
## Simulate data from t0

## simulate the same number of data that in january
n_jan <- filter(holes_data, date == "janv. 2016") %>%
    group_by(species) %>%
    summarise(n= n())

## Simulation
simul_t0 <- inner_join(summary_sp_0, n_jan) %>%
    mutate(simul = pmap(list(n, mean, sd),
	    function(n, mean, sd) rnorm(n = n, mean = mean, sd = sd))) %>%
    ungroup() %>%
    select(-n, -mean, -sd) %>%
    unnest() %>%
    mutate(date = "nov. 2015") #%>%
#    spread(key = variable, value = simul)

```

```{r rgr_computation, echo = FALSE}
## RGR data  building

## first method
holes_data2 <- inner_join(holes_data, mean_sp_0) %>%
    mutate(ln_d = log(d) - log(d0),
	ln_h = log(h) - log(h0),
	ln_hm = log(hm) - log(h0),
	duration = yearmon2month(date),
	rgr_d = ln_d/duration,
	rgr_h = ln_h/duration,
	rgr_hm = ln_hm/duration
	)

rgr_data <- select(holes_data2, -ln_d, -ln_h, -ln_hm, -duration, -d0, -h0, -hm , -h, -d) %>% ungroup() %>%
    mutate(
	date_m = month(date),
	duration_m = date_m + 2)

rgr_t0 <- filter(rgr_data, date != "nov. 2016", surv != 0) %>%
ungroup() %>%
mutate(date_m = month(date),
duration = date_m + 2,
rgr_d1 = rgr_d + 1)
unique(holes_data2$species)

## Second method
rgr2 <- group_by(holes_data, label, species, com, ms, watering) %>%
  arrange(date) %>%
  mutate(
    diff_d = c(NA,diff(d)),
    diff_h = c(NA,diff(h)),
    diff_hm = c(NA,diff(hm)),
    ln_d = c(NA,diff(log(d))),
    ln_h = c(NA,diff(log(h))),
    ln_hm = c(NA,diff(log(hm)))
    ) %>%
  mutate(
      duration = yearmon2month(date),
      month_lag = c(NA,diff(as.integer(duration))),
      agr_d = diff_d/month_lag,
      agr_h = diff_h/month_lag,
      agr_hm = diff_hm/month_lag,
      agr_d1 = agr_d + 1,
      rgr_d = ln_d/month_lag,
      rgr_h = ln_h/month_lag,
      rgr_hm = ln_hm/month_lag,
      rgr_d1 = rgr_d + 1
  ) %>%
  filter(date != "janv. 2016") %>%
  ungroup()


agr2_summary <- gather(rgr2, key = "variable", value = "value", agr_d, agr_h,
  agr_hm) %>%
group_by(duration, species, com, ms, watering, variable) %>%
summarise(
  mean = mean(value, na.rm = TRUE),
  ic_width = 1.96*sd(value, na.rm = TRUE)/sqrt(n())
)

rgr2_summary <- gather(rgr2, key = "variable", value = "value", rgr_d,
  rgr_h, rgr_hm) %>%
group_by(duration, species, com, ms, watering, variable) %>%
summarise(
  mean = mean(value, na.rm = TRUE),
  ic_width = 1.96*sd(value, na.rm = TRUE)/sqrt(n())
)

```

```{r}
rgr2 %>%
  ggplot(aes(x = as.factor(date), y = agr_d)) +
  geom_boxplot(aes(linetype = watering, colour = ms)) +
  ylab("AGR of basal diameter") +
  ggplot2::facet_grid(com ~ species)
```


```{r}
# ind data surv
#load("../data/try2.RData")
data(try2)
try2_ok <- try2 %>%
    mutate(date_m = month(date), duration_m = date_m + 2) %>%
    mutate(
	surv = ifelse(survival == 0, TRUE, FALSE),
	com = ifelse(com %in% c("A", "D", "P"), "Mono", "Poly"),
	ms = ifelse(ms == "0", "Open", "Patch"),
	watering = ifelse(watering == "0", "No Watered", "Watered"),
	watering = as.factor(watering),
	species = as.factor(species)
	)
# Holes data surv
holes_data_surv <- holes_data2  %>%
    mutate(date_m = month(date), duration_m = date_m + 2)

# Holes data surv summary
holes_data_surv_summary <- holes_data2  %>%
    mutate(date_m = month(date),
	duration_m = date_m + 2) %>%
    group_by(duration_m, ms, com, watering, species) %>%
    summarise(
	mean = mean(surv, na.rm = T),
	ic_width = 1.96*sd(surv, na.rm = T)/sqrt(n())
	)

```

## Data selection

### RGR max

```{r pre_rgr_boxplot, echo = FALSE}
p <- ggplot(rgr2,
    aes(x = as.factor(date), y = rgr_d)) +
    geom_boxplot(aes(linetype = watering, colour = ms)) +
    ylab("RGR of basal diameter")
p + ggplot2::facet_grid(com ~ species)

```
```{r pre_rgr_plotmeans, echo = FALSE}
p <- ggplot(filter(rgr2_summary, variable == "rgr_d"),
    aes(x = duration, y = mean, colour = ms, linetype = watering)) +
    geom_line() + geom_point() +
    geom_errorbar(aes(ymin = mean - ic_width, ymax = mean + ic_width), width = 0.025)
p + facet_grid(com ~ species)
```
```{r data_mois, echo = FALSE}
rgr2_march  <- filter(rgr2, date == "mars 2016") %>%
    select(ter, plot, label,  ms, com, watering, species, rgr_d, duration) %>%
    mutate(rgr_d1 = rgr_d +1)
rgr2_t0_janv  <- filter(rgr_t0, date == "janv. 2016") %>%
    select(ter, plot, label,  ms, com, watering, species, rgr_d, duration) %>%
    mutate(rgr_d1 = rgr_d +1)

```

## Analysis

### Gradient CS

```{r gradient_CS_plot, echo = FALSE}
p <- ggplot(filter(holes_data_surv_summary, ms == "Open", watering == "No Watered"),
    aes(x = duration_m, y = mean, colour = species)) +
    geom_line() + geom_point() +
    geom_errorbar(aes(ymin = mean - ic_width, ymax = mean + ic_width), width = 0.025) +
    labs(colour = "") + # Remove legend title
    theme(legend.position = "bottom")

p + facet_grid(com ~.)

legend <- get_legend(p)
legend_b <- get_legend(p + theme(legend.position = "bottom"))
legend_t <- get_legend(p + theme(legend.position = "top"))

g1 <- p + facet_grid(com ~.) +
    surv_graph_conf +
    conf
g2 <- plot_grid(
    g1,
    legend_b,
    nrow = 2,
    rel_heights = c(9, 1)
    )

save_plot(filename = "cs_gradient.pdf",
    plot = g2,
    base_height = 71,
    base_width = 71, # make room for figure legend
    path = "~/Documents/thesis/papers/spain_diversity/figures",
    unit = "mm"
    )
```
```{r gradient_CS_table, echo = FALSE}
#holes_data_surv_summary
holes_data_surv_summary_open <- filter(holes_data_surv_summary, ms == "Open")%>%
    ungroup() %>%
    select(-ms) %>%
    mutate(duration_m = as.factor(duration_m))

surv_table_ok <- xtable(holes_data_surv_summary_open)
label(surv_table_ok) <- c("tab:surv")
digits(surv_table_ok) <- c(1,1,1,1,1, 2, 2)
caption(surv_table_ok) <- paste("Proportion of survival summary according to
    the duration of the experiment and the variable manipulated.", sep="")

print(surv_table_ok, include.rownames = FALSE,
    file = "~/Documents/thesis/papers/spain_diversity/surv_table.tex")

```

## Survival

```{r survival, echo = FALSE, eval = FALSE}
holes_data_surv2  <- filter(holes_data_surv, ms == "Open") %>% ungroup() %>%
    mutate(species = as.factor(species))
try_data_surv  <- filter(try2_ok, ms == "Open")
test <- survfit(Surv(holes_data_surv2$duration_m, surv) ~ species + com +
    watering, holes_data_surv2)
plot(test)
str(test)

lm_surv <- survdiff(Surv(holes_data_surv2$duration_m, surv) ~ com + ms +
    watering, holes_data_surv2, rho=0)
summary(lm_surv)

my.surv <- Surv(try2_ok$duration_m, try2_ok$surv)
my.fit <- summary(survfit(my.surv ~ 1))
coxph.fit <- coxph(my.surv ~ species * com * watering, data = try2_ok,
    method="breslow")
coxph.fit
anova(coxph.fit)

test <- summary(coxph.fit)
ajusted_r_squared <- round(test$rsq[1], 2)
test2 <- test$coefficients
term <- dimnames(test2)[[1]]
term
term2 <- c("dorycnium", "pistachia", "com", "watering", "dorycnium:com",
    "pistachia:com", "dorycnium:watering", "pistachia:watering", "com:watering",
    "dorycnium:com:watering", "pistachia:com:watering")

test3 <- as_tibble(test2) %>%
    mutate(Factor = term2) %>%
select(Factor, coef, `exp(coef)`, `se(coef)`, z, `Pr(>|z|)`) %>%
    rename(`$\\beta$` = coef, `$e^\\beta$` =`exp(coef)`, SE = `se(coef)`,
	`Z-values` = z, `P-values` = `Pr(>|z|)`)

cox_table_ok <- xtable(test3)
label(cox_table_ok) <- c("tab:cox")
digits(cox_table_ok) <- c(1, 1, 2, 2, 2, 3, 4)
caption(cox_table_ok) <- paste("Summary of the Cox proportional hazards. The adjusted R squared equaled to $", ajusted_r_squared, "$.",
    sep="")

print(cox_table_ok, include.rownames = FALSE, sanitize.colnames.function =
    identity, file = "~/Documents/thesis/papers/spain_diversity/cox_table.tex")

```

```{r}
library(glmmTMB)
surv <- glmmTMB(survival ~ ms + duration_m + species + com + watering + (1 + ms|plot), data = try2_ok, family = "binomial")

surv_by_plot <- holes_data2 %>%
    mutate(
      date_m = month(date),
      duration_m = date_m + 2,
      duration_m = as.factor(duration_m),
      ter = as.factor(ter),
      plot = as.factor(plot),
      com = as.factor(com),
      ms = as.factor(ms),
      ) %>%
    group_by(duration_m, ms, com, watering, species, ter, plot) %>%
    summarise(prop_surv = mean(surv, na.rm = T))


summary_surv_by_plot <- surv_by_plot %>%
    group_by(duration_m, ms, com, watering, species) %>%
    summarise(
      mean = mean(prop_surv, na.rm = T),
      ci = sd(prop_surv, na.rm = T) / sqrt(n())
      )

summary_surv_by_plot %>%
  ggplot(aes(y = mean, x = duration_m, color = ms, linetype = watering)) +
  geom_point() +
  geom_errorbar(aes(ymin = mean - ci, ymax = mean + ci), width = 0.025) +
  facet_grid(com ~ species)

# interaction
int_surv <- surv_by_plot %>%
  ungroup() %>%
  spread(ms, prop_surv) %>%
  mutate(surv_n_int_a = map2_dbl(Open, Patch, n_int_a))

# Data unbalanced at plot scale for watering
filter(surv_by_plot, duration_m == 3, com == "Mono", ter == 3, plot == 10) %>%
  spread(ms, prop_surv)

summary_int_surv <- int_surv %>%
    group_by(duration_m, com, watering, species) %>%
    summarise(
      mean = mean(surv_n_int_a, na.rm = T),
      ci = sd(surv_n_int_a, na.rm = T) / sqrt(n())
      )

int_surv %>%
  filter(duration_m %in% c(8, 13)) %>%
  ggplot(aes(y = surv_n_int_a, x = as.factor(duration_m), color = species, linetype = watering)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  facet_grid(com ~ .)

surv_mod <- lmer(
  formula = surv_n_int_a ~ duration_m + com + species + watering  + (1|ter/plot),
  data = filter(int_surv, duration_m %in% c(8, 13))
)

mySumm2 <- function(.) {
  c(beta=fixef(.),sigma=sigma(.), sig01=sqrt(unlist(VarCorr(.))))
}
surv_boot <- bootMer(surv_mod, mySumm2, nsim = 100)
surv_ci <- confint(surv_boot)
#surv_colin <- car::vif(surv_mod) not use if one response
surv_sum <- piecewiseSEM::rsquared(surv_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggeffects::ggpredict(surv_mod,
  terms = c("species", "duration_m", "watering", "com"),
  type = "fe")
surv_pred <- pred %>%
  as_tibble() %>%
  rename(
    n_int_a = predicted,
    species = x,
    duration_m = group,
    watering= facet,
    com = panel
  )

surv_pred %>%
  ggplot(aes(
      y = n_int_a,
      x = as.factor(duration_m),
      color = species, linetype = as.factor(com))) +
  geom_point(position = position_dodge(width = 0.9)) +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
      position = position_dodge(width = 0.9), width = .2) +
  facet_grid(cols = vars(watering)) +
  geom_jitter(
    position = position_dodge(width = 0.9),
    data = int_surv %>%
      rename(n_int_a = surv_n_int_a) %>%
      filter(duration_m %in% c(8, 13)),
    inherit.aes = TRUE)
```


# Results

## RGR d

```{r anova, echo = FALSE}

anova_data <- filter(rgr_t0, duration == 5)

## LMER
test <- lmer(rgr_d ~ ms + watering + com + species + (1 | plot), anova_data)
test2 <- lmer(rgr_d ~ ms*species + watering + com + species + (1 | plot), anova_data)
test3 <- lmer(rgr_d ~ ms*species + watering*species + com + (1 | plot), anova_data)
test4 <- lmer(rgr_d ~ ms*species + watering*species + com*species + (1 | plot), anova_data)
test5 <- lmer(rgr_d ~ ms*species*watering*com + (1 | plot), anova_data)

anova(test, test2, test3, test4, test5)
summary(test5)

## LM
test <- lm(rgr_d ~ ms + watering + com + species , anova_data)
test2 <- lm(rgr_d ~ ms*species + watering + com + species , anova_data)
test3 <- lm(rgr_d ~ ms*species + watering*species + com , anova_data)
test4 <- lm(rgr_d ~ ms*species + watering*species + com*species , anova_data)
test5 <- lm(rgr_d ~ ms*species*watering*com , anova_data)

anova(test, test2, test3, test4, test5)
summary(test5)

anova_table <- anova(test5)
anova_table2 <- tidy(anova_table) %>%
    mutate(stars = p_stars(p.value)) %>%
 arrange(desc(statistic)) %>%
    rename(Factor = term, DF = df, SS = sumsq, MS = meansq, "F-values"
	= statistic, "P-values" = p.value, "sig. lvl" = stars)

anova_table3 <- glance(anova_table)

anova_table_ok <- xtable(anova_table2)
label(anova_table_ok) <- c("tab:anova")
digits(anova_table_ok) <- c(1, 1,1, 4, 4, 2, 4, 1)
ajusted_r_squared <- round(summary(test5)$adj.r.squared, 2)
caption(anova_table_ok) <- paste("ANOVA summary of the complete model from the
    experiment (all the manipulated variable and the interactions between them)
    considering the basal diameter RGR of march. The adjusted R squared is $",
    ajusted_r_squared, "$. DF: Degree of freedom, SS: Sum of Squares, MS: Means
    of Squares, *: \\textit{P} < 0.05, **: \\textit{P} < 0.01 and ***:
    \\textit{P} < 0.001. species: identity of the sapling (Anthyllis cytisoides,
	Dorycnium pentaphyllum or Pistachia lentiscus), com: diversity of the
    sapling community composition (monospecific or multispecies community),
    watering: intermittent water supplementation (yes of no), ms: microsite
    (open or patch).", sep="")

print(anova_table_ok, include.rownames = FALSE,
    file = "~/Documents/thesis/papers/spain_diversity/anova_table.tex")

```
```{r pseudo_pairs, echo = FALSE, eval = TRUE}
data(try2)
holes_pairs <- filter(try2, date == "janv. 2016", ind == "1") %>%
    select(ter, label, ms, com, watering) %>%
    group_by(ter, com, watering) %>%
    arrange(label) %>%
    nest()

##dataset to choose:
# - rgr2 or rgr2_march: d or rgr(t) = (ln(X_t) - ln(X_{t-1}))/(T_t - T_{t-1})
# - rgr_t0 or rgr_t0_janv: rgr(t) = (ln(X_t) - ln(X_{t-1}))/(T_t - T_0)
dataset_ok <- rgr2
## Choose response variable
var_rep <- "agr_d1"
## Choose explicative variable
var_exp <- c("label", "species", "ms", "com", "watering", "duration")

# Make the pairs
holes_pairs2 <- holes_pairs %>%
    mutate(pair = purrr::map(data, pair_find)) %>%
    unnest(pair) %>%
    mutate(
	pair_id = as.numeric(rownames(.)),
	Patch = as.integer(Patch),
	Open = as.integer(Open)
	)

# Make open and patch dataset
test <- select_(dataset_ok, .dots = c(var_rep, var_exp))

## Open dataset
test_open <- filter(test, ms == "Open", label %in% holes_pairs2$Open) %>%
    left_join(., select(holes_pairs2, Open, pair_id) %>% rename(label = Open)) %>%
    arrange(pair_id) %>%
    ungroup() %>%
    select(-ms, - label) %>% rename_(Open = var_rep)
## Patch dataset
test_patch <- filter(test, ms == "Patch", label %in% holes_pairs2$Patch) %>%
    left_join(., select(holes_pairs2, Patch, pair_id) %>% rename(label =
	    Patch)) %>%
    arrange(pair_id) %>%
    ungroup() %>%
    select(-ms, - label) %>% rename_(Patch = var_rep)
## Join dataset
paired_data <- left_join(test_open, test_patch)
paired_index <- paired_data %>%
    mutate(n_int_a = map2_dbl(Open, Patch, n_int_a)) %>%
    select(-Open, -Patch)

paired_index_summary <- paired_index %>%
    group_by(duration, species, com, watering) %>%
    summarise(
	mean = mean(n_int_a, na.rm = TRUE),
	sd = sd(n_int_a, na.rm = TRUE),
	ic_width = 1.96*sd/sqrt(n())
      	)

```

```{r}
growth_plot <- rgr2 %>%
  mutate(
    date_m = month(date),
    duration_m = date_m + 2,
    duration_m = as.factor(duration_m),
    ter = as.factor(ter),
    plot = as.factor(plot),
    com = as.factor(com),
    ms = as.factor(ms)
    ) %>%
  group_by(duration_m, ms, com, watering, species, ter, plot) %>%
  summarise(agr_d1 = mean(agr_d1, na.rm = T))

int_growth <- growth_plot %>%
  ungroup() %>%
  spread(ms, agr_d1) %>%
  mutate(agr_n_int_a = map2_dbl(Open, Patch, n_int_a))

int_growth %>%
  ggplot(aes(y = agr_n_int_a, x = as.factor(duration_m), color = species, linetype = watering)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  facet_grid(com ~ .)

growth_mod <- lmer(
  formula = agr_n_int_a ~ duration_m + com + species + watering + (1|ter/plot),
  data = int_growth
)

mySumm2 <- function(.) {
  c(beta=fixef(.),sigma=sigma(.), sig01=sqrt(unlist(VarCorr(.))))
}
growth_boot <- bootMer(growth_mod, mySumm2, nsim = 100)
growth_ci <- confint(growth_boot)
#growth_colin <- car::vif(growth_mod) not use if one response
growth_sum <- piecewiseSEM::rsquared(growth_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggeffects::ggpredict(growth_mod,
  terms = c("species", "duration_m", "watering", "com"),
  type = "fe")
growth_pred <- pred %>%
  as_tibble() %>%
  rename(
    n_int_a = predicted,
    species = x,
    duration_m = group,
    watering= facet,
    com = panel
  )

growth_pred %>%
  ggplot(aes(
      y = n_int_a,
      x = as.factor(duration_m),
      color = species, linetype = as.factor(com))) +
  geom_point(position = position_dodge(width = 0.9)) +
  geom_hline(yintercept = 0) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
      position = position_dodge(width = 0.9), width = .2) +
  facet_grid(cols = vars(watering)) +
  geom_jitter(
    position = position_dodge(width = 0.9),
    data = int_surv %>%
      rename(n_int_a = surv_n_int_a) %>%
      filter(duration_m %in% c(8, 13)),
    inherit.aes = TRUE)

```


## Survival analysis


## Dist to optimum

```{r plot_duration, echo = FALSE}
p <- ggplot(filter(paired_index, com == "Mono"),
    aes(x = as.factor(duration), y = n_int_a)) +
    geom_violin(aes(fill = species)) +
    #geom_errorbar(aes(ymin = mean - ic_width, ymax = mean + ic_width), width = 0.025)+
    ylab("Interaction index (NIntA)")
p + facet_grid(. ~ watering)

```
```{r plot_duration2, echo = FALSE}
p <- ggplot(paired_index,
    aes(x = as.factor(duration), y = n_int_a, color = species, linetype = com)) +
    geom_boxplot() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")
p + facet_grid(. ~ watering)

```
```{r dist_opt_cor, echo = FALSE}
dist2opt_temp <- paired_index
dist2opt_table <- group_by(dist2opt_temp, com, watering, duration) %>%
    mutate(rank_sp = as.numeric(as.factor(species))) %>%
    summarise(
	spearman = cor( x = rank_sp, y = n_int_a, method = "spearman",
	   use = "pairwise.complete.obs"),
       spearman.p = cor.test( x = rank_sp, y = n_int_a, method = "spearman",
	   use = "pairwise.complete.obs", alternative = "greater", exact =
	       FALSE)$p.value)

#map2_dbl(rank_sp, n_int_a, cor, method = "spearman")
test_table <-  mutate(dist2opt_table,
    species = "dorycnium",
    n_int_a = 0.4,
    spearman = round(spearman, 3),
    spearman.p = round(spearman.p, 4)
    )

g1 <- p + facet_grid(com ~ watering) +
    geom_text(data = test_table,
	aes(label = paste("Spearman~~", "rho==", spearman, "~~P==", spearman.p,
		sep = "")), #, " = ", spearman, ", P = ", spearman.p
	size = letter_size -1,
	parse = TRUE # Important to display math
	)
g1
#save_plot(filename = "dist_optimum.pdf",
    #plot = g1,
    #base_height = 100,
    #base_width = 140, # make room for figure legend
    #path = "~/Documents/thesis/papers/spain_diversity/figures",
    #unit = "mm"
    #)

```

## Diversity effect

```{r div_effect_plot_sp, echo = FALSE}
p <- ggplot(paired_index,
    aes(x = as.factor(duration), y = n_int_a, color= com)) +
    geom_violin() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")
p + facet_grid(species ~ watering)
```
```{r div_effect_test, echo = FALSE}
div_effect_temp <- paired_index
div_effect_table <- group_by(div_effect_temp, species, watering, duration) %>%
    spread(com, value = n_int_a) %>%
    do(tidy(wilcox.test(.$Mono, .$Poly, na.rm= TRUE))
       ) %>%
    mutate(n_int_a = 0.4, com = "Poly",
	stars = p_stars(p.value),
	p.value = round(p.value, 3))

```
```{r div_effect_plot_sp2, echo = FALSE}
g1 <- p + facet_grid(. ~ watering) +
    geom_text(data = div_effect_table,
	aes(label = paste(stars,
		sep = "")),
	size = letter_size -1,
	parse = FALSE # Important to display math
	) +
    theme(axis.text.x = element_text(angle=-45, hjust=0))
g1
```
```{r div_effect_test_tot, echo = FALSE}
div_effect_table_tot <- group_by(div_effect_temp) %>%
    spread(com, value = n_int_a) %>%
    do(tidy(wilcox.test(.$Mono, .$Poly, na.rm= TRUE))
       )%>%
    mutate(n_int_a = 0.4, com = 1.5,
	p.value = round(p.value, 3))
```
```{r div_effect_plot_tot, echo = FALSE}
p <- ggplot(filter(paired_index, duration == 5),
    aes(x = com, y = n_int_a)) +
    geom_violin() +
    ylab("Interaction index (NIntA)") +
    geom_hline(yintercept = 0, color = "red")

g2 <- p + geom_text(data = div_effect_table_tot,
	aes(label = paste("Wilcoxon~~", "W==", statistic, "~~P==", p.value,
		sep = "")), #, " = ", spearman, ", P = ", spearman.p
	size = letter_size -1,
	parse = TRUE # Important to display math
	)

```
```{r div_effect_plot_gather, echo = FALSE}
g3 <- plot_grid(g1, g2, labels = "auto", align = 'h', rel_widths =
    c(1, 0.5))

g3
#save_plot(filename = "div_effect.pdf",
    #plot = g3,
    #base_height = 71,
    #base_width = 140, # make room for figure legend
    #path = "~/Documents/thesis/papers/spain_diversity/figures",
    #unit = "mm"
    #)

```

## Dominance effect  

Test if in poly there is a negative correlation of NIntA between species

```{r div_dominance_correlation, echo = FALSE}
dominance_data <- int_surv %>%
  select(-Open, - Patch) %>%
  filter(com == "Poly", duration_m %in% c(8, 13)) %>%
  spread(species, value = surv_n_int_a)

cor(select(dominance_data, anthyllis:pistachia),
  use = "pairwise.complete.obs", method = "spearman")
```

## Traits

```{r}
mypath <- rprojroot::find_package_root_file
source(mypath("inst", "doc", "misc.R"))
traits <- read_csv2(mypath("data-raw","data_mars_traits.csv"))

traits %>%
  select(sp1, fresh_mass1, fresh_m_f1, sp2, fresh_mass2, fresh_m_f2)
# Dorycnium does not have measurement without petiole

 %>% is.na(.)
map(c("1", "2", "3"), function (x) {

  expe_trt <- c("ter", "plot", "label", "ms", "com", "watering")
  col_in_sp <- str_match(names(traits), x) %>% .[,1]
  tmp <- trait[, names(traits) %in% c(expe_trt, col_in_sp)]

  col_fresh_mass <- c(paste0("fress_mass", x), paste0())
  tmp %>%

  })
```


# Appendices

```{r allometry_assessment, echo = FALSE}
data <- read.table("../../data-raw/biomass_t0.csv", sep=";", dec=",", header=T)

data[, "biomass"] <- data[, "bio_stem"] + data[, "bio_roots"] + data[, "bio_leaves"]
data[, "diameter"] <- ( data[, "dia1"] + data[, "dia2"] )/2

variable <- c("diameter")        #Explicative variables
# , "Vegetative height (cm)"

par(pch=20, mfrow=c(1,2))
pdf(file = "~/Documents/thesis/papers/spain_diversity/figures/allometry.pdf", width = 6, height = 6)
for (i in 1:length(variable)) {
	plot( data[data$species=="Dorycnium", "biomass"] ~ data[data$species=="Dorycnium", variable[i]],
		xlab="Basal diameter (mm)", ylab="Total biomass (g)",
		ylim=range(data$biomass), xlim=range(data[,variable[i]])
		)
	points(data[data$species=="Anthyllis", "biomass"] ~ data[data$species=="Anthyllis", variable[i]], col="red")
	points(data[data$species=="Pistacia", "biomass"] ~ data[data$species=="Pistacia", variable[i]], col="green")
	abline(lm(data[data$species=="Anthyllis", "biomass"] ~ data[data$species=="Anthyllis", variable[i]] ), col="red")
	abline(lm(data[data$species=="Dorycnium", "biomass"] ~ data[data$species=="Dorycnium", variable[i]] ), col="black")
	abline(lm(data[data$species=="Pistacia", "biomass"] ~ data[data$species=="Pistacia", variable[i]] ), col="green")

}
dev.off()

mod <- lm(biomass ~ diameter + diameter:species , data)
mod <- lm(biomass ~ diameter*species , data)
summary(mod)

```

## Number of holes available

Number of holes in which there is still at least one sapling alive

```{r holes_alive_time, echo = FALSE, fig.width=8, fig.height=4}
n_data_date <- holes_data %>%
    mutate(date_m = month(date),
    duration_m = date_m + 2) %>%
    group_by(duration_m, species, ms, com, watering) %>%
    filter(surv != 0) %>%
    summarise(n_count = n())

g <- ggplot(n_data_date,
    aes(y = n_count, x = duration_m, fill = species, colour = ms, alpha = com)) +
    geom_bar(stat="identity", position = "dodge")+
    labs(x = "Number of months since the beginning of the experiment", y =
	"Count")
g + facet_grid(. ~ watering)

save_plot(filename = "nb_holes_alive.pdf",
    plot = g,
    base_height = 71,
    base_width = 140, # make room for figure legend
    path = "~/Documents/thesis/papers/spain_diversity/figures",
    unit = "mm"
    )
```

## RGR time series

```{r rgr_time_series, echo = FALSE}
rgr_summary <- gather(rgr_t0, key = "variable", value = "value", rgr_d,
    rgr_h, rgr_hm) %>%
    group_by(duration_m, species, com, ms, watering, variable) %>%
    summarise(
	mean = mean(value, na.rm = TRUE),
	ic_width = 1.96*sd(value, na.rm = TRUE)/sqrt(n())
      	)

p <- ggplot(filter(rgr_summary, variable == "rgr_d"),
    aes(x = duration_m, y = mean, colour = ms, linetype = watering)) +
labs(x = "Number of months since the beginning of the experiment", y = "Basal
    diameter RGR (mm.month^-1)") +
    geom_line() + geom_point() +
    geom_errorbar(aes(ymin = mean - ic_width, ymax = mean + ic_width), width = 0.025)
p2 <- p + facet_grid(com ~ species)
p2

save_plot(filename = "rgr_d_data_series.pdf",
    plot = p2,
    base_height = 100,
    base_width = 160, # make room for figure legend
    path = "~/Documents/thesis/papers/spain_diversity/figures",
    unit = "mm"
    )

```

