---
title: "Survival analysis"
output:
  pdf_document:
    highlight: zenburn
    fig_width: 4
    fig_height: 4
    fig_caption: true
    toc: true
    toc_depth: 3
    number_sections: true
  geometry: margin=2cm
  word_document:
    highlight: zenburn
    fig_width: 4
    fig_height: 4
    fig_caption: true
    toc: true
---

# Resume

I analyzed the data according to the `vignette("adjcurve")`. Firstly, we wanted
to test if the survival curves are different according to the variables designed
in the experiment. 


```{r loading}
library(tidyverse)
library(magrittr) #use pipe
library(zoo)
library(survival)
library(survminer)

devtools::load_all()
data(holes_data)

```

# Data transformation

The data are summarized by holes and by species. For survival, it results that the survival
variable (`surv`) can take the values `r round(unique(holes_data$surv), 1)` in
the monoculture treatment but `r round(unique(holes_data[holes_data$com ==
"Poly",]$surv), 1)` in polyculture. To overcome this problem, we transformed the
survival variable in binomial 0/1 data in monoculture. It means that we analyzed
the occurrence of the first dead in the hole.

```{r transform_data}
holes_data %<>% select(-hm, -d, -h) %>%
    mutate(death = ifelse(surv == 1, 0, 1), 
	duration = yearmon2month(date))# needed in survival package 

```

```{r basic_survfit}
sfit <- survfit(Surv(time = duration, event = death) ~ ms + species + com + watering, holes_data)

g <- survminer::ggsurvplot(sfit, data = holes_data)
curv_facet <- g$plot + facet_grid(ms ~ com  + watering)
curv_facet
```

# Open


# Complete model

```{r Kaplan-Meyer_analysis, echo = FALSE}
#Fit
sfit <- survfit(Surv(time = duration, event = death) ~ interaction(ms,species,watering,com), holes_data)
ssfit <- surv_summary(sfit)
# TODO: faire un beau plot facet_grid pour la survie
#Test
#sdiff <- survdiff(Surv(time = duration, event = death) ~ interaction(ms,species,watering,com), holes_data)
#summary(sdiff)

```

```{r cox_hazard_analysis, eval = FALSE}
#http://www.sthda.com/english/wiki/cox-proportional-hazards-model
#Fit
coxfit <- coxph(Surv(time = duration, event = death) ~
    interaction(ms,species,watering,com), holes_data) 
summary(coxfit)

#Test
#sdiff <- survdiff(Surv(time = duration, event = death) ~
    #interaction(ms,species,watering,com), holes_data) 
#summary(sdiff)

```

## Plant plant interaction effects on survival
