---
title: ""
author: "Alain Danet, Susana Bautista, ..., Fabien Anthelme, Sonia Kéfi"
date: ""
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
  officedown::rdocx_document:
bibliography: "bibliography.bib"
#csl: "nature.csl"
link-citations: true
toc: false
linestretch: 2.0
---


<!--always_allow_html: true-->
<!--header-includes:-->
  <!--- \usepackage[left]{lineno}-->
  <!--- \linenumbers-->
  <!--- \hypersetup{backref=true}-->

```{r setup, include=FALSE}
library(rmarkdown)
library(officedown)
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      comment = "#>",
                      fig.path = "graphics/knitr-",
                      fig.retina = 1.618, # Control using dpi
                      fig.width = 6,  # generated images
                      fig.pos = "H",  # pdf mode
                      #fig.align = "center",
                      dpi = if (knitr::is_latex_output()) 72 else 300,
                      out.width = "100%",
                      dev = "png",
                      dev.args = list(png = list(type = "cairo-png")),
                      optipng = "-o1 -quiet")

library(here)
source(here::here("R","basic_stat.R"))
source(here::here("R","inla_helpers.R"))
source(here::here("R","clean_data.R"))
source(here::here("R","string_replacements.R"))
library(tidyverse)
library(magrittr)
library(cowplot)
library(targets)
library(kableExtra)
library(coda)
library(ggbreak)


if (Sys.info()["login"] == "alain") {
  file.copy(
    from = "~/Documents/post-these/references.bib",
    to = here("paper", "bibliography.bib")
  )
}
```

# Introduction

# Material & Methods


# Results

```{r load-targets, include=FALSE}
tar_load(c(inla_surv_odd, bm_inla_scaled_effects, bm_inla_effects))
```

```{r}
s_t <- get_effect_ci(effect = inla_surv_odd, term = "duration_m", ci_lvl = "0.95")
s_c <- get_effect_ci(effect = inla_surv_odd, term = "comPoly", ci_lvl = "0.80")
s_cm <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch", ci_lvl = "0.95")
s_m <- get_effect_ci(effect = inla_surv_odd, term = "msPatch", ci_lvl = "0.80")
s_w <- get_effect_ci(effect = inla_surv_odd, term = "wateringWatered", ci_lvl = "0.95")
s_wm <- get_effect_ci(effect = inla_surv_odd, term = "msPatch:wateringWatered", ci_lvl = "0.80")
s_wc <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:wateringWatered", ci_lvl = "0.90")
s_wcm <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
s_dor <- get_effect_ci(effect = inla_surv_odd, term = "speciesdorycnium", ci_lvl = "0.95")
s_pis <- get_effect_ci(effect = inla_surv_odd, term = "speciespistachia", ci_lvl = "0.95")
unique(inla_surv_odd$term)
```

```{r}
plot_inla_fixed_effect(inla_surv_odd, color_var = NULL, intercept = 1) +
  labs(x = "Odd-ratios (exp(beta))") +
  theme(axis.title.y = element_blank())
```

Being in a patch (i.e. under an adult plant of *Artemisia herba-alba*) did not
change the odds of sapling survival (Odd-Ratio: `r s_m`) in monoculture, but we found a
positive effect of patch location in diverse communities (OR = `r s_cm`).
However, the diversity of the sapling communities did not affect the odds of
survival (OR = `r s_c`) overall. Watering treatment was associated with higher
odds of survival (strong evidence, OR = `r s_w`), and hastened in
diverse communities (moderate evidence, OR = `r s_wc`). We did not find evidence
that the effect of the watering treatment on odds change in patch (OR = `r s_wm`), we
found strong evidence that the watering treatment decreased the positive effect
of sapling community diversity under *A. herba-alba* on survival likelihood (OR
= `r s_wcm`). We finally found that survival odds varied across species,
*Pistachia lentiscus* and *Dorycnium pentaphyllum* having lower survival overall
(OR = `r s_pis`, `r s_dor` respectively). We further found that treatments
affects differently the species (See Fig. SXX).

```{r}
plot_inla_fixed_effect(bm_inla_effects %>% filter(response == "bm"),
  color_var = NULL, intercept = 0) +
  labs(x = "Slope Coefficients") +
  theme(axis.title.y = element_blank())
```

```{r}
bm_effects <- bm_inla_effects %>% filter(response == "bm")
b_t <- get_effect_ci(effect = bm_effects, term = "duration_m", ci_lvl = "0.95")
b_t2 <- get_effect_ci(effect = bm_effects, term = "I(duration_m^2)", ci_lvl = "0.95", r = 4)
b_m <- get_effect_ci(effect = bm_effects, term = "msPatch", ci_lvl = "0.80")
b_cm <- get_effect_ci(effect = bm_effects, term = "comPoly:msPatch", ci_lvl = "0.80")
b_c <- get_effect_ci(effect = bm_effects, term = "comPoly", ci_lvl = "0.95")
b_wc <- get_effect_ci(effect = bm_effects, term = "comPoly:wateringWatered", ci_lvl = "0.90")
b_w <- get_effect_ci(effect = bm_effects, term = "wateringWatered", ci_lvl = "0.80", r = 4)
b_wm <- get_effect_ci(effect = bm_effects, term = "msPatch:wateringWatered", ci_lvl = "0.80")
b_wcm <- get_effect_ci(effect = bm_effects, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
b_dor <- get_effect_ci(effect = bm_effects, term = "speciesdorycnium", ci_lvl = "0.95")
b_pis <- get_effect_ci(effect = bm_effects, term = "speciespistachia", ci_lvl = "0.95")
```

Using estimated biomass from basal diameter and vegetative height, we found
a continuous increase in biomass until June (Standardized coefficient: $\beta$'=
`r b_t`) and that biomass decreaded from June to November (second order effect
of time, $\beta$'=`r b_t2`). We did not find evidence that being in patch
changed the sapling biomass ($\beta$'=`r b_m`), and this effect was not modulated by
community diversity ($\beta$' = `r b_cm`). We further found weak evidence that
watering decreased the joint effect of patch and diversity on sapling biomass
`r b_wcm`. We found strong evidence that the biomass of saplings was lower in
diverse communities ($\beta$' = `r b_c`), but it was counteracted by watering
(medium evidence, $\beta$' = `r b_wc`). Watering was found to have a positive
effect on sapling biomass (weak evidence, $\beta$' = `r b_w`).

```{r}
tar_load(leaf_inla_effects_scaled)
ldmc_effects <- leaf_inla_effects_scaled %>%
  filter(response == "ldmc")

sla_effects <- leaf_inla_effects_scaled %>%
  filter(response == "sla")

a_m <- get_effect_ci(effect = sla_effects, term = "msPatch", ci_lvl = "0.90")
l_m <- get_effect_ci(effect = ldmc_effects, term = "msPatch", ci_lvl = "0.90", r = 3)

a_cm <- get_effect_ci(effect = sla_effects, term = "comPoly:msPatch", ci_lvl = "0.80")
a_c <- get_effect_ci(effect = sla_effects, term = "comPoly", ci_lvl = "0.95")
a_wc <- get_effect_ci(effect = sla_effects, term = "comPoly:wateringWatered", ci_lvl = "0.90")
a_w <- get_effect_ci(effect = sla_effects, term = "wateringWatered", ci_lvl = "0.80", r = 1)
a_wm <- get_effect_ci(effect = sla_effects, term = "msPatch:wateringWatered", ci_lvl = "0.80")
a_wcm <- get_effect_ci(effect = sla_effects, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
a_dor <- get_effect_ci(effect = sla_effects, term = "speciesdorycnium", ci_lvl = "0.95")
a_pis <- get_effect_ci(effect = sla_effects, term = "speciespistachia", ci_lvl = "0.95")

l_cm <- get_effect_ci(effect = ldmc_effects, term = "comPoly:msPatch", ci_lvl = "0.80")
l_c <- get_effect_ci(effect = ldmc_effects, term = "comPoly", ci_lvl = "0.95")
l_wc <- get_effect_ci(effect = ldmc_effects, term = "comPoly:wateringWatered", ci_lvl = "0.90")
l_w <- get_effect_ci(effect = ldmc_effects, term = "wateringWatered", ci_lvl = "0.95", r = 1)
l_wm <- get_effect_ci(effect = ldmc_effects, term = "msPatch:wateringWatered", ci_lvl = "0.80")
l_wcm <- get_effect_ci(effect = ldmc_effects, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
l_dor <- get_effect_ci(effect = ldmc_effects, term = "speciesdorycnium", ci_lvl = "0.95")
l_pis <- get_effect_ci(effect = ldmc_effects, term = "speciespistachia", ci_lvl = "0.95")
```

```{r}
plot_inla_fixed_effect(ldmc_effects, color_var = NULL)
plot_inla_fixed_effect(leaf_inla_effects_scaled)
```

Leaf traits was found to vary across patch and watering treament. We found
moderate evidence that saplings Leaf Dry Matter Content decreased and that
Specific Leaf Area increased in patch ($\beta$' = `r l_m` and `r a_m`
respectively), meaning that saplings develop a more "resource exploitive"
strategy (or a "resource conservative" strategy) in patches. We further found
strong evidence that LDMC was lower in watered treatment ($\beta$' = `r l_w`)
not SLA ($\beta$' = `r a_w`). Overall, we did not find evidence that community
diversity affected leaf traits.

## Plant-plant interactions

Using the predictions of the model, we found that the outcome of  interactions
between saplings and *Artemisia herba-alba* were driven by interactive effects
between the diversity of sapling communities and the watering trement (The
effects are consistent through time, see Fig. SXX).
We found that competitive interactions dominated in single species communities
non watered for both survival and biomass. In watered sites, the single species
communities were found to have positive or less have negative
interactions in terms of survival and biomass respectively. In diverse
communities non-watered, we found positive interactions both in terms survival
and biomass, but strongly negative interactions in watered sites.

Beyond those general effects at the community level, we found strong disparities
using a model at the species level. In single species communities no watered, we
found that neutral and negative competitive interactions dominated for *A.
citisoides* and *D. pentaphyllum*, but positive interactions for *P. lenticus*
in terms of survival, for all species displayed negative interactions in terms
of biomass. We found strong discrepanties among species in the watered sites,
*A. citisoides* was the most facilited followed by *D. pentaphyllum* and
competition for *P. lenticus* in term of survival, we found the opposite gradient
in term of biomass, *P. lenticus* being the most facilitated and  *A.
citisoides* displaying the strongest competitive effects. In diverse
communities non watered, we found that *P. lenticus* and *A. citisoides* displayed
strong positive interactions in term of survival while *D. pentaphyllum*
displayed negative interactions, while  *A. citisoides* and *D. pentaphyllum*
displayed positive interactions in terms of biomass but *P. lenticus* displayed
negative interactions. In watered diverse communities, *A. citisoides* and *D.
pentaphyllum* both displayed negative interactions with *A. herba-alba* in terms
of survival and biomass while *P. lenticus* displayed positive in terms of
survival but negative in terms of biomass.


```{r}
tar_load(pp_int_global)
p_int_global <- pp_int_global %>%
  filter(duration_m == 5, response %in% c("survival", "bm")) %>%
  ggplot(aes(y = inta, ymin = inta_low, ymax = inta_high,
      x = species, color = com, shape = watering)) +
  geom_pointrange(position = position_dodge(.5)) +
  geom_hline(yintercept = 0) +
  facet_grid(cols = vars(response)) +
  theme_bw()
```


```{r}
tar_load(pp_int)
int_surv <- pp_int %>%
  filter(response %in% c("survival"))
p_int_surv <- int_surv  %>%
  ggplot(aes(y = inta, x = duration_m + 6, color = com, linetype = watering, fill = com), alpha = 1) +
  geom_line() +
  geom_hline(yintercept = 0) +
  geom_ribbon(aes(ymin = inta_low, ymax = inta_high), alpha = .5) +
  facet_grid(cols = vars(species), scales = "free_y") +
  theme_bw()

p_int_bm <- pp_int %>%
  filter(response == "bm") %>%
  ggplot(
    aes(
      y = inta, ymin = inta_low, ymax = inta_high,
      x = species, color = com, shape = watering,
      group = watering,
      fill = com
      ),
    alpha = 1, position = "dodge") +
  geom_hline(yintercept = 0) +
  geom_pointrange(position = position_dodge(.5)) +
  theme_bw()

p_int_sp <- plot_grid(
  p_int_surv,
  p_int_bm
)
```

```{r}
plot_grid(p_int_global, p_int_sp, nrow = 2)
```



```{r, eval = FALSE}
# Supplementary to show that interaction does not change through time
pp_int %>%
  filter(response %in% c("bm", "d", "survival", "h")) %>%
  ggplot(aes(y = inta, x = duration_m + 6, color = com, linetype = watering, fill = com), alpha = 1) +
  geom_line() +
  geom_ribbon(aes(ymin = inta_low, ymax = inta_high), alpha = .5) +
  facet_grid(cols = vars(species), rows = vars(response), scales = "free_y") +
  theme_bw()
```

```{r}
tar_load(biomass_modelling)
tar_load(biomass_modelling_r2)
tar_load(biomass_t0)

biomass_t0$bm_total_pred <- exp(predict(biomass_modelling$log_mod_bm_tot_h))
biomass_t0 %>%
  ggplot(aes(x = bm_total, y = bm_total_pred, color = species)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0)

biomass_t0 %>%
  ggplot(aes(y = log(bm_total), x = log_d, color = species)) +
  geom_point() +
  geom_smooth(method = "lm")
biomass_t0 %>%
  ggplot(aes(y = log(bm_total), x = log_h, color = species)) +
  geom_point() +
  geom_smooth(method = "lm")
```

# Discussion

Our study aimed to scale plant-plant interactions among saplings and adult plant
at the community level. To do so, we planted sapling communities of three
individuals in open sites or below the canopy of an adult individual of *A.
herba-alba*. We manipulated the diversity and the input of water to the sapling
communities. Using a hierarchical bayesian model accounting for variation
at the plot and site level, we found that diverse communities had
higher survival and biomass in terms of survival and biomass, an evidence of
strong facilitative effects. We further found that watering downplayed the
positive effect of being under an adult of *A. herba-alba*, resulting in
negative interactions. At the species level, we found strong variations in the
response to watering and diversity in terms of survival and biomass,
suggesting an interplay between stress-tolerance and competitive abilities
of sapling species.

## Diversity, patch and watering

We found that higher diversity of sapling species enhances facilitation at the
community scale. More specifically, only *Pistachia lenticus* displayed a
relatively weak facilitation in single species treatment in term of survival.
This results is accordance with previous studies showing that communities
located under nurse plants tend to have higher species richness (REF). This
result can be explain by the possible decrease in niche overlap among saplings
in diverse communities [ref], which in turn decrease competition for resource
exploitation and may increase the benefits of facilitation [ref].

Watering is found to modulate strongly the outcome of the interactions among
saplings and *Artemisia herba-alba*. In monospecific communities, watering
switched the sign of the interactions from negative to relatively weakly
positive for survival. A reason might be that the added water was hold
longer under the canopy of *A. herba-alba*. Possible mechanisms include
lower evapotranspiration under the canopy due to the shading.
Watering was found to increase the overall survival of sapling and we found weak
evidence that watering enhances further the survival of sapling in *A.
herba-alba* patches, which lend toward the hypothesis of higher watering benefit
under *A. herba-alba*.

However, watering was found to drive competition in diversity-rich sapling
communities, i.e. an opposite effect from monospecific communities. More
specifically, we found that watering treatment had more positive effects on
survival and biomass in diverse communities while watering was decreasing the
positive effect of being in a patch and in diverse communities. Hence, watering
seems to make that diverse sapling communities experiment more competition than
facilitation from *A. herba-alba*. This result is in line with the
Stress-Gradient-Hypothesis that propose that positive interactions should
predominate in more benign environment [@bertness_stress_1994]. Interestingly,
it was not the case in single species communities which suggests that biotic
stress, i.e. intraspecific interactions among saplings, play an important role
in driving the outcome of interactions between saplings and *A. herba-alba*.

The consideration of both abiotic stress and among sapling competition might
then be the key to understand observed outcome sapling-shrub interactions.
Previous studies showed that biotic stressors such as grazing can lead to the
pattern of SGH alike abiotic stressors[@smit; @graff; @mart]. Further conceptual
development highlighted that multiple stressors can drive plant-plant interactions,
such as resource (e.g. water) or non resource (e.g. temperature, wind) and
biotic stressors (e.g. grazing) [@]. However, a missing link is the
consideration of competition between the plants that benefit from the nurse
plant, which can be considered as another type of biotic stress. We then propose a
framework including both interactions among the beneficiary plants and the level
of abiotic stress (Fig. XXa). Competition between sapling community and adult
shrub should dominate when both abiotic stress and competition among saplings
is strong are high or low. Then, facilitation between sapling community and
adult shrub are expect to arise when either by decreasing abiotic stress (e.g.
by watering in our experiment, Fig. XXa from 4 to 3) or by decreasing
competition inside the beneficiary community (e.g. by increasing diversity in
our experiment, Fig. XXa from 4 to 2). We can then map both abiotic stress and
competition among saplings on a single gradient dimension to explain how
the joint effects of watering and community diversity can affect the outcome of
sapling-shrub interactions in the original framework of the SGH [@bertness;
@maestre]. As understory communities were reported to be composed of numerous
species [ref], the consideration of the competition inside understory
communities might help us to understand the mechanisms driving the assembly of
understory communities in natural communities [].

We further found species variations in their response to the
treatments. (Give some example).
However, we did not find evidence of a relationship between stress-tolerance
of the species and the outcome of sapling-shrub interactions [@graff;
@liancourt]. According to this hypothesis, *P. lenticus*, *D. pentaphyllum* and
*A. citisoides*, that had lower to the highest survival in the open sites,
should have respectively experiment the highest from the lower facilitation in
single species treatment. In turn,


# Conclusion & perspectives


# References
