---
title: "Species richness and abiotic stress interact to drive plant-plant interactions"
author: "Alain Danet, Susana Bautista, ..., Fabien Anthelme, Sonia Kéfi"
date: ""
output:
  officedown::rdocx_document:
    base_format: "bookdown::word_document2"
    number_sections: false
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
bibliography: "bibliography.bib"
#csl: "nature.csl"
link-citations: true
toc: false
linestretch: 2.0
---


<!--always_allow_html: true-->
<!--header-includes:-->
  <!--- \usepackage[left]{lineno}-->
  <!--- \linenumbers-->
  <!--- \hypersetup{backref=true}-->

```{r setup, include=FALSE}
library(rmarkdown)
library(officedown)
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      comment = "#>",
                      fig.path = "graphics/knitr-",
                      fig.retina = 1.618, # Control using dpi
                      fig.width = 6,  # generated images
                      fig.pos = "H",  # pdf mode
                      #fig.align = "center",
                      dpi = if (knitr::is_latex_output()) 72 else 300,
                      out.width = "100%",
                      dev = "png",
                      dev.args = list(png = list(type = "cairo-png")),
                      optipng = "-o1 -quiet")

library(here)
source(here::here("R","basic_stat.R"))
source(here::here("R","inla_helpers.R"))
source(here::here("R","clean_data.R"))
source(here::here("R","string_replacements.R"))
library(tidyverse)
library(magrittr)
library(cowplot)
library(targets)
library(kableExtra)
library(coda)
library(ggbreak)


if (Sys.info()["login"] == "alain") {
  file.copy(
    from = "~/Documents/post-these/references.bib",
    to = here("paper", "bibliography.bib"),
    overwrite = TRUE
  )
}
```

# Abstract {-}



# Introduction {-}

Understanding the effects of global change on biodiversity is a central question
in Ecology. Climate change in particular has already tremendous effects on
ecological communities and its effects are projected to be to more dramatic in
the years and decades to come. Many places already become drier and experience
more frequent extreme drought event, driving the failure of recruitment of new
individuals and excess in mortality. Understanding how climate change effects on
biodiversity is therefore crucial for biodiversity conservation^[I tried to adapt to the angle of the [special issue](https://www.oikosjournal.org/blog/call-papers-role-plant-facilitation-mediating-climate-change-impact-biodiversity)].

Stressors such as resource shortage or extreme temperatures are affecting
dramatically species physiology and metabolism. In turn, species physiology and
metabolism also determine species interactions. Such example includes the
balance between competition and facilitation among plants along a stress
gradient [@bertness_positive_1994]. The Stress-Gradient-Hypothesis proposed that
competitive interactions dominates in both begnin and highly stressful
environment while facilitation dominates at intermediate levels of stress
[@bertness_positive_1994]. Plants providing positive interactions, generally
referred to as "benefactors" or "nurses", can have direct positive effects on
other plants by improving the environmental conditions beneath their canopy,
e.g. by decreasing the soil erosion, buffering the daily fluctuations in
temperature, and increasing water retention [@callaway_positive_2007]. Positive
interactions among plants was reported to increase species richness
[@gross_positive_2008; @cavieres_facilitative_2014], increase diversity of
community composition [@kikvidze_effects_2015] and shown to have a tremendous
role on ecosystem properties such as productivity [@cardinale_species_2002;
@wright_overlooked_2017] and resilience [@kefi_spatial_2007; @kefi_local_2007].
Improving our understanding of the effects of stressors in ecological
communities then necessitates to account for their effects on species
interactions.

The question of the universality has been questionned, experiment studies
reporting contrasting results [@maestre_does_2005; @lortie_re-analysis_2006].
Previous studies reported that the appearance of positive interactions in
stressful environments is modulated by the source of stress (resource, non
resource, or herbivory) [@maestre_refining_2009; @smit_inclusion_2009] and by
the strategies of the plants involved in the interactions. Previous studies
reported that the most mal-adapted species are the more facilitated
[@liancourt_stress_2005; @graff_species_2017]. Indirect interactions among
beneficiary plants can also alter the net effect of the interactions between
nurse and sapling [@schob_direct_2013; @michalet_direct_2017], they can
modulate species coexistence and the species dominance [@levine_indirect_1999;
@levine_beyond_2017]. Taking in account both the strategy of the species in
interaction and the interactions among beneficiary species is therefore a step
forward a better understanding of the balance between competition and
facilitation in ecological communities.

Coexistence theory predicts that competition among species is decreased when
they have lower niche overlap (i.e. higher niche differentiation)
[@macarthur_limiting_1967; @chesson_mechanisms_2000]. In turn, beneficiary
communities having a higher niche complementarity should maximize the benefits
of habitat amelioration provided by a nurse plants. In turn, species rich
beneficiary communities may exhibit more positive interactions than species poor
beneficiary communities. As far as we know, this hypothesis has not been tested
experimentally. The interplay between the strength of the competition among
beneficiary species and the level of environmental stress might be one key to
understand the community assembly in stressful environment.

We tested how the Stress-Gradient-Hypothesis is modulated by the diversity of
the beneficiary communities. To do so, we conducted a one year sapling transplant
experiment in a Mediterranean steppeland in Spain. In a fully factorial design,
we transplanted sapling communities in open sites or below shrubs, We used three
beneficiary species which were expected to vary in terms of their tolerance to
water stress. We manipulated the composition of the sapling communities,
planting monospecific communities for each of three species and diverse
communities with the three species present. We finally manipulated water
supplementation, to alter the level of abiotic stress experienced by the sapling
communities. We followed survival, basal diameter and vegetative height, but
also measured the functional traits.

# Material & Methods {-}

```{r exp, fig.cap = "Experimental design"}
knitr::include_graphics(here("paper", "graphics", "experimental_design2.pdf"))
```

## Study area {-}

The experiment was conducted at a field site in the Murcia region, Southeastern
Spain (37°57’33"N, 1°00’17"W – 172 m a.s.l., Fig. \@ref(fig:exp)b). Climate is
semiarid Mediterranean with a very high interannual variability. Annual rainfall
follows a bimodal distribution, with two rainy seasons (spring and autumn) and a
very dry and warm summer. Mean annual rainfall is 297 mm with mean monthly
rainfall ranging from 3 mm in July to 36 mm in October. Mean annual temperature
is 18.6 °C with monthly averages ranging from 10.6 °C in January to 27.6 °C in
August (Murcia Meteorological Station, 38°00'7''N - 1°10'15''W- 61 m a.s.l.;
period: 1984-2010). Soils are thin (20-50 cm), silt-loam (32\% sand, 47\% silt,
21\% clay), and basic (pH = 8.7), developed over marls. The area is a mosaic of
moderately steep slopes covered by alpha-grass (\textit{Stipa tenacissima})
steppes and abandoned agricultural terraces built on the streambeds. The
terraces in the study site were abandoned in the 80s and 90s and progressively
colonized by forbs and shrubs. At present, the perennial vegetation is dominated
by the shrub species \textit{Artemisia herba-alba} and \textit{Anthyllis
cytisoides}, which can be found either as monospecific patches of one or a few
individuals or coexisting in multispecies patches. Marginal goat grazing occurs
in the area. \textit{A. herba-alba} shrubs are not palatable and may exert a
positive effect on the highly palatable species \textit{A. cytisoides} by
protecting young individuals from both goat grazing and predation by the
European rabbit (\textit{Oryctolagus cuniculus}), which is the dominant native
herbivore in the area [@verwijmeren_drought_2014].

## Experimental design {-}

To test if benefactor-sapling interactions are linked to the capacity of the
saplings to endure stress, we selected three common shrub species of the
Mediterranean steppes as beneficiary species, namely \textit{Anthyllis
cytisoides}, \textit{Dorycnium pentaphyllum} and \textit{Pistacia lentiscus},
which are commonly found to co-occur [@amat_community_2015]. \textit{A.
cytisoides} and \textit{D. pentaphyllum} are Fabaceae and \textit{P. lentiscus}
belongs to the Anacardiaceae family. All those species have characteristics
which are usually depicted as favorable to endure arid climate. \textit{A.
cytisoides} is a drought-avoider, dropping its leaves during the summer thereby
decreasing the transpiring area [@haase_photosynthetic_2000]. \textit{P.
lentiscus} is a late successional evergreen shrub which can develop a dense root
system at the sapling stage within their year of planting
[@maestre_positive_2003]. It can also increase the water storage in its
leaves during the bad season [@maestre_mechanisms_2004], the thick cuticle
of its leaves [@coste_flore_1937] limiting the loss of water by
evapotranspiration. \textit{D. pentaphyllum} is a low-growing species known for
its resistance to water stress [@caravaca_use_2003]. Its leaves are
composed by segments, decreasing the transpiring surface.

The saplings were grown in the open air in a nursery located at 30 km from the
study site (Viveros Muzalé S.L., Abanilla, Spain). They were grown in controlled
wet conditions in 200 ml containers with a mixture of peat and coconut fiber.
There were about 6 months at the time of transplantation. The benefactor
species, \textit{A. herba-alba}, is a pioneer shrub and common non-palatable
species which is pioneer in deserts [@alados_association_2006].

---
# http://www.viverosmuzale.com/catalogo/info/anthyllis_cytisoides.html
# http://www.viverosmuzale.com/catalogo/info/dorycnium_pentaphyllum.html
# http://www.viverosmuzale.com/catalogo/info/pistacea_lentiscus.html
---

Three variables were manipulated: the community diversity,
the water supply and the microsite where the sapling communities were set (Fig. \@ref(fig:exp)b). The
sapling species variable had three modalities: \textit{A. cytisoides}, \textit{D.
pentaphyllum} and \textit{P. lentiscus}. The community diversity variable had two
modalities: monospecific and multispecies, and the water supply two as well: yes
or no. Finally, the microsite variable had two modalities: open or patch (i.e.
beneath the canopy of \textit{A. herba-alba}). Overall, we had 16 treatment
combinations ($4 \times 2 \times 2$). The treatment combinations were replicated
20 times and distributed within 3 main terraces (Fig. \@ref(fig:exp)c)
comprising respectively 7, 7 and 6 replicates.

Because of the abundance of grazers in the area (mainly rabbits), all the
terraces were fenced with $1.80$ meters height wire grid fences and reinforced
by chicken wire extending from about 60 cm above ground to 20 cm below ground.
The transplantation took place from 23 October to 4 November 2015, on planting
holes of approximately $25 \times 25 \times 25$ cm that were dug manually. The
holes corresponding to the patch treatment were located beneath the canopy of a
benefactor, about 20 cm apart from the main stem of the plant, and oriented
north to maximize the shading effect. One week before the beginning of the
plantation, the area received about 40 mm of natural rainfall, which provided
excellent initial moisture conditions for the introduced saplings. The holes
were randomly attributed to the different treatments. We planted three plants
per hole, following a triangular arrangement in which the plants were equally
distant from each other (around 10 cm). The containers, in which the plants came
from the green house,  contained each several individuals. To exclude the
mortality due to the transplant shock in the further analysis, we only kept the
holes in which at least one individual from the original container was alive in
January.  We removed the supernumerary individuals by cutting their stems at the
basis. The watering treatment was applied in January, March, April, May, June,
July, August and October 2016 by putting 1.5 L of water by hole.

We recorded the survival, basal diameter and vegetative height from January to
October 2016 (10 months). We further measured Leaf Dry Matter Content (LDMC) and
Specific Leaf Area (SLA) in March 2016 (4 months after the plantation)
following recommendations [@perez-harguindeguy_new_2013]. We collected only
leaves in good shape, mature and the most exposed to the sunbeam. Furthermore,
we tried to collect only on the individuals which had sufficient leaves to not
suffer of the sampling (subjective point of view). We collected 3 leaves by *P.
lentiscus*, 5 leaves by *A. citisoides* and 10 leaves by *D. pentaphyllum* by
respect to the weight of species leaves.  Leaves from each individuals were
stored in a falcon tube with a humid tissue to limit dessication, all the falcon
being stored in a thermal isolated box. At the laboratory, we first rehydrated
them with deionized water during several minutes. Following this, we weighted
the leaves and scanned them, and finally dried them at least 48h at 72 celcius
degrees. We then measured their dry weight to compute LDMC and SLA. We randomly
selected sites to be sampled, we finally reach from 7 to 36 samples for SLA,
from 13 to 75 for LDMC by treatment combination (Table SXX).

---
# see
# /home/alain/Documents/thesis/alicante/thesis_chap2_alicante/inst/examples/experiment.rmd
---

```{r}
tar_load(biomass_modelling_r2)
r2bm <- setNames(round(unlist(biomass_modelling_r2[1,][c(2, 3)]), 2), c("R2", "adj"))
```


Prior to the experiment, we collected twelve individuals of each species for
which we measured total biomass. There was several individuals in each container and
their number were variable. We selected the biggest stem to do our
measurements. We measured the height of the stem, we took two perpendicular measurements
of basal diameter. We then separated the stem, the leaves and the roots and
dried then at 65°C during 3 days to obtain the biomass. Following allometric
relationship, we estimated the relationship between total biomass, basal
diameter and vegetative height with a species effect. The R2 of the model were
quite high (R2 = `r r2bm["R2"]`, adjusted R2 = `r r2bm["adj"]`). We further
found good relationship between predicted and observed values (Fig. SXX).


\begin{equation}
  \begin{gather}
    B = \beta_0 \times \beta_1\exp{d} \times \beta_2\exp{h} \times \sum{\beta_{2 + j}S_j}\\
    \log B = \beta_0 + \beta_1 \log d + \beta_2 \log h + \sum{\beta_{2 + j}S_j}
  \end{gather}
  (\#eq:bm)
\end{equation}


## Data analysis {-}

### Statistical model {-}

We modelled the response variable using hierarchical Bayesian models. We included as predictors the
diversity, watering and patch treatments ($\sum_{k=1}\beta_k X_k$), as well as
the interactions among them (double interactions:
$\sum_{k=1, k \neq l}\beta_{kl} X_k X_l$, and triple interactions:
$\sum_{k=1, k \neq l, l \neq k}\beta_{klm} X_k X_l X_m$). We added time, i.e.
number of month since the start of the experiment ($\beta_0Time_t$),
species identity ($\sum_{s}\beta_{s}S_s$) and the terrace as control
predictors ($\sum_{j}\beta_{j}T_j$).

\begin{equation}
  \begin{gather}
     Y_{i|p,z,t} = \alpha + \beta_0Time_t + \sum_{s}\beta_{s}S_s + \sum_{j}\beta_{j}T_j +\\
     \sum_{k=1}\beta_k X_k + \sum_{k=1, k \neq l}\beta_{kl} X_k X_l +\\
     \sum_{k=1, k \neq l, l \neq k}\beta_{klm} X_k X_l X_m +\\
     \epsilon_{i|p,z,t}
  \end{gather}
  (\#eq:gen)
\end{equation}

- $\alpha = \alpha_0 + a_{p|j} + a_{i|p|j}$
- $a_{p|j}, a_{i|p|j}, \epsilon_{i|p,z,t} \sim \mathcal{N}(0,\,\sigma^{2})$
- $j$: terrace, $p$: plot, $i$: site, $t$: time $t$

We added random effects on the intercept to capture the variation associated
with the hierarchical structure of the experimental design. We accounted for
random variations at the plot level (nested in the terrace level, $a_{p|j}$) and
the site level (nested in the terrace and plot levels, $a_{i|p|j}$). We removed
random variations at the plot level for biomass as its effects was too small to
be correctly estimated.

All models except survival were modelled using a Gaussian response. The
probability of survival ($p$) was modelled as a Binomial response with a logit
link (i.e. $logit(p) = \log \dfrac{p}{1-p}$). We further added a quadratic
effect of time to model biomass as biomass was found to decrease after summer.
We used a version of the model at the species level, i.e. accounting for the
different effects of the treatments across species. To do so, we added an
interaction between each predictor ($X_k$) and species identity $S_s$, as well
as their interactions. This model at the species level allowed us to further
explore how each species reacted to the treatment combination, but is complex
because it includes fourth way interactions ($\sum_{k=1, k \neq l, l \neq k,
s}\beta_{klm} X_k X_l X_m S_s$).

Before the analysis, we centered time variable to march (month number 5) in
order to get estimated coefficients at a relevant values. The diversity of the
sapling community, species identity, site (open / patch), and watering were
factorial variables. Their reference values were respectively single species, *A.
citisoides*, open site, and no watered.

The models were evaluated in a Bayesian framework using Integrated Nested
Laplacian Approximation [@rue_approximate_2009; @rue_bayesian_2017] (INLA). We
computed the credible intervals at 80%, 90% and 95% using the Highest Posterior
Density method[@hyndman_computing_1996], which can respectively be interpreted
as weak, moderate and strong evidence of an effect when the interval does not
include 0 [@van_klink_meta-analysis_2020; @mastrandrea_guidance_2010]. The
statistical models were implemented using the `INLA` R
package [@rue_approximate_2009], with defaults uninformative priors. The prior
distribution of fixed coefficients followed a flat zero centred normal
distribution ($\mathcal{N}(\mu,\, \sigma^2) = \mathcal{N}(0,\, 1000)$). The
prior distribution of the random effects and the gaussian error
($\epsilon_{it}$, eq. \@ref(eq:gen)) followed a log gamma distribution with
shape and inverse scale parameters ($\mathcal{G}(s, \, \tau) = \mathcal{G}(1, \,
5.10^-5)$). We then back-transformed the estimated coefficients to to the
standard deviations attributed to the random effects and the gaussian error
($\sigma = 1 / \sqrt{\tau}$).

We checked the overall quality of the model fit to the data by plotting the
fitted versus the observed values (Fig. SXX). We visually inspected the PIT and
CPO (respectively Posterior Integral Transform and Conditional Predictive
Ordinate) distribution to assess both the quality of data representation, and
the frequency of outliers.

We computed $R^2$ to assess the quality of the fit of the bayesian models. We
then computed marginal ($R^2_m$) and conditional ($R^2_c$) R-squared,
respectively associated to the variance explained by fixed effects and the one
explained by both fixed and random effects[@nakagawa_general_2013]. We only
included the random effects on the intercept in the $R^2$ computation, i.e. the
plot effect ($a_{p|j}$) and the site effect ($a_{i|p|j}$), as the inclusion of the
variance attributed to random slopes is much more complex and was shown to not change
the results [@nakagawa_general_2013; @lahuis_explained_2014]. We computed the
variance associated with each predicted value from their posterior distribution,
following recommendations to take in account the variability associated with
the priors [@gelman_r-squared_2019]. We then reported the mean marginal and
conditional $R^2$ associated the 95% credible interval computed using the
Highest Posterior Density method. We did not compute $R^2$ for survival models
as they do not contain residuals errors^[I did not know! [source 1](https://stats.stackexchange.com/a/3562), [source 2](https://stats.stackexchange.com/a/124826)] (as logistic regression predicts a
probability of survival while the data are binary).

$$
R^2_m = \dfrac{Var_{fit}}{Var_{fit} + Var_{res}} = \dfrac{\sigma^2(\hat{y_i})}{\sigma^2(\hat{y_i}) + \sigma^2(y_i - \hat{y_i})}
$$

$$
R^2_c = \dfrac{Var_{fit} + (a_{p|j})^2 + (a_{i|p|j})^2}{Var_{fit}  + (a_{p|j})^2 + (a_{i|p|j})^2 + Var_{res}}
$$

$y_i$ and $\hat{y_i}$ being respectively the observations and the predicted
values, $Var_{fit}$ and $Var_{res}$ being respectively the variance of
predictive means and the variance of the residuals [@gelman_r-squared_2019].
$a_{p|j}$ and $a_{i|p|j}$ are respectively the standard deviation on the random
intercept associated to the plot and the site.


### Interaction strength {-}

The net effect of the benefactor-beneficiary interactions was estimated with the
Neighbor-effect Intensity index
[NInt\textsubscript{A}, @diaz-sierra_new_2016]. This index satisfies
several mathematical properties which are important such as (i) standardization
which allows comparisons between different species, (ii) symmetry which ensures
that the same quantity removed or added will have the same effect on the index,
(iii) boundedness and (iv) the possibility of computing an estimation error. All
those properties are shared by the NInt\textsubscript{A} and are also shared by
another commonly used index, the RII [@armas_measuring_2004]. The
NInt\textsubscript{A} and the RII only differ from each other by their type of
symmetry, respectively additive and commutative. The additive symmetry makes
that, for example, an increase or decrease in performance of ten (i.e., +10 or
-10) will be translated in the same amount of variation by the
NInt\textsubscript{A} index whereas in the case of a commutative symmetry in
RII, it is the multiplicative effect of performance which will be translated in
the same amount of variation (for example a performance multiplied by 10 and
divided by 10), resulting in a underestimation of the positive effects
[@diaz-sierra_new_2016]. The NInt\textsubscript{A} is computed as follows:

\begin{equation}
    NInt_A = 2 \frac{ \Delta P }{P_{-N} + |\Delta P|}
    (\#eq:int)
\end{equation}

with $P$ being the performance of the target species, in open sites ($P_{-N}$)
and the difference between the performance in patches and in open sites $\Delta
P$.

The performance of the species were extracted from the prediction of the models.
We used the mean predicted values and their credible interval at 95% to compute the net
effects of sapling-benefactor interaction. The predicted probability of survival
and the predicted biomass were respectively used to compute the net effect of
interaction for survival and biomass respectively. We further computed the net
effect using the model at the community level and at the species level, the
latter was used to explore the variation of the net effect across species.

# Results {-}

```{r load-targets, include=FALSE}
tar_load(c(inla_surv_odd, bm_inla_scaled_effects, bm_inla_effects))
```

```{r}
s_t <- get_effect_ci(effect = inla_surv_odd, term = "duration_m", ci_lvl = "0.95")
s_c <- get_effect_ci(effect = inla_surv_odd, term = "comPoly", ci_lvl = "0.80")
s_cm <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch", ci_lvl = "0.95")
s_m <- get_effect_ci(effect = inla_surv_odd, term = "msPatch", ci_lvl = "0.80")
s_w <- get_effect_ci(effect = inla_surv_odd, term = "wateringWatered", ci_lvl = "0.95")
s_wm <- get_effect_ci(effect = inla_surv_odd, term = "msPatch:wateringWatered", ci_lvl = "0.80")
s_wc <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:wateringWatered", ci_lvl = "0.90")
s_wcm <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
s_dor <- get_effect_ci(effect = inla_surv_odd, term = "speciesdorycnium", ci_lvl = "0.95")
s_pis <- get_effect_ci(effect = inla_surv_odd, term = "speciespistachia", ci_lvl = "0.95")
```

```{r}
p_surv <- plot_inla_fixed_effect(inla_surv_odd, color_var = NULL, intercept = 1) +
  labs(x = "Odd-ratios (exp(beta))") +
  theme(axis.title.y = element_blank())
```

```{r}
tar_load(c(surv_data_modelling, inla_surv_pred, inla_surv_sp_pred))
p_pred_surv <- surv_data_modelling %>%
  group_by(duration_m, ms, com, watering, species, plot) %>%
  summarise(survival = sum(survival) / n()) %>%
  ggplot(aes(y = survival, x = duration_m + 6, color = com, shape = watering)) +
  geom_jitter(alpha = .2) +
  geom_line(data = inla_surv_sp_pred, aes(y = mean)) +
  geom_point(data = inla_surv_sp_pred, aes(y = mean)) +
  facet_grid(cols = vars(species), rows = vars(ms)) +
  labs(
    x = "Number of month since the start of the experiment",
    y = "Probability of survival",
    color = "Diversity",
    shape = "Watering") +
  theme_bw() +
  theme(legend.position = "bottom")
p_pred_effect_surv <- plot_grid(p_surv, p_pred_surv, rel_widths = c(.4, 1))
ggsave(
  filename = "p_pred_effect_surv.pdf",
  plot = p_pred_effect_surv,
  path = here("paper", "graphics"),
  scale = 2.4,
  width = 90,
  height = 90 * .6,
  units = "mm",
  dpi = "print"
)
```

Being in a patch (i.e. under an adult plant of *Artemisia herba-alba*) did not
change the odds of sapling survival (Odd-Ratio: `r s_m`, Fig. \@ref(fig:sbm)a)
in monoculture, but we found a positive effect of patch location in diverse
communities (OR = `r s_cm`, Fig. \@ref(fig:sbm)a). However, the diversity of the sapling communities
did not affect the odds of survival (OR = `r s_c`) overall. Watering treatment
was associated with higher odds of survival (strong evidence, OR = `r s_w`), and
hastened in diverse communities (moderate evidence, OR = `r s_wc`). We did not
find evidence that the effect of the watering treatment on odds change in patch
(OR = `r s_wm`), we found strong evidence that the watering treatment decreased
the positive effect of sapling community diversity under *A. herba-alba* on
survival likelihood (OR = `r s_wcm`). We finally found that survival odds varied
across species, *Pistacia lentiscus* and *Dorycnium pentaphyllum* having lower
survival overall (OR = `r s_pis`, `r s_dor` respectively). We further found that
treatments affects differently the species (Fig. \@ref(fig:sbm)b, See Fig. SXX
for the effects). For example, *P. lentiscus* had the highest increase in
survival in the watering treatment [Probably add more examples].

```{r, fig.cap = "Biomass"}
tar_load(c(bm_inla_pred, bm_inla_sp_pred))
p_bm <- plot_inla_fixed_effect(bm_inla_effects %>% filter(response == "bm"),
  color_var = NULL, intercept = 0) +
  labs(x = "Slope Coefficients") +
  theme(axis.title.y = element_blank())
p_pred_bm <- surv_data_modelling %>%
  group_by(duration_m, ms, com, watering, species, plot) %>%
  summarise(bm = mean(bm, na.rm = TRUE)) %>%
  ggplot(aes(y = bm, x = duration_m + 6, color = com, shape = watering)) +
  geom_jitter(alpha = .2) +
  geom_line(data = bm_inla_sp_pred %>% filter(response == "bm"), aes(y = mean)) +
  geom_point(data = bm_inla_sp_pred %>% filter(response == "bm"), aes(y = mean)) +
  facet_grid(cols = vars(species), rows = vars(ms)) +
  labs(
    x = "Number of month since the start of the experiment",
    y = "Biomass",
    color = "Site",
    shape = "Watering") +
  theme_bw() +
  theme(legend.position = "bottom")
p_pred_effect_bm <- plot_grid(p_bm, p_pred_bm, rel_widths = c(.4, 1))
ggsave(
  filename = "p_pred_effect_bm.pdf",
  plot = p_pred_effect_bm,
  path = here("paper", "graphics"),
  scale = 2.4,
  width = 90,
  height = 90 * .6,
  units = "mm",
  dpi = "print"
)
```

```{r}
leg_pred <- get_legend(p_pred_surv)
p_pred_effect <- plot_grid(
  plot_grid(p_surv, p_pred_surv + theme(legend.position = "none"),
    rel_widths = c(.5, 1), labels = c("a", "b")),
  plot_grid(p_bm, p_pred_bm + theme(legend.position = "none"),
    rel_widths = c(.5, 1), labels = c("c", "d")),
  leg_pred,
  rel_heights = c(1, 1, .1),
  ncol = 1)
ggsave(
  filename = "p_pred_effect.pdf",
  plot = p_pred_effect,
  path = here("paper", "graphics"),
  scale = 2.4,
  width = 90,
  height = 90 ,
  units = "mm",
  dpi = "print"
)
```

```{r}
fig_surv_bm <- paste0("Slope of the statical models at the community level (left panel, a \\& c) and prectictions at the species level (right panel, b \\& d) for (a \\& b)
  survival and (c \\& d) biomass. Survival coefficients (a) are the exponential of odd-ratios, values below and above 1 display respectively negative and positive effect on survival probability. Left panels: points represent the mean of the posterior distribution of coefficients; Thin, medium and large bars represent the credible interval at 95\\%, 90\\% and 80\\%. Right panels display the predictions of the model at the species level (See methods), points display the data averaged by plot (N = 12).") %>%
str_replace_all("\\s+", " ")
```


```{r sbm, fig.cap=fig_surv_bm}
knitr::include_graphics(here("paper", "graphics", "p_pred_effect.pdf"))
```



```{r}
bm_effects <- bm_inla_effects %>% filter(response == "bm")
b_t <- get_effect_ci(effect = bm_effects, term = "duration_m", ci_lvl = "0.95")
b_t2 <- get_effect_ci(effect = bm_effects, term = "I(duration_m^2)", ci_lvl = "0.95", r = 4)
b_m <- get_effect_ci(effect = bm_effects, term = "msPatch", ci_lvl = "0.80")
b_cm <- get_effect_ci(effect = bm_effects, term = "comPoly:msPatch", ci_lvl = "0.80")
b_c <- get_effect_ci(effect = bm_effects, term = "comPoly", ci_lvl = "0.95")
b_wc <- get_effect_ci(effect = bm_effects, term = "comPoly:wateringWatered", ci_lvl = "0.90")
b_w <- get_effect_ci(effect = bm_effects, term = "wateringWatered", ci_lvl = "0.80", r = 4)
b_wm <- get_effect_ci(effect = bm_effects, term = "msPatch:wateringWatered", ci_lvl = "0.80")
b_wcm <- get_effect_ci(effect = bm_effects, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
b_dor <- get_effect_ci(effect = bm_effects, term = "speciesdorycnium", ci_lvl = "0.95")
b_pis <- get_effect_ci(effect = bm_effects, term = "speciespistachia", ci_lvl = "0.95")
```

Using estimated biomass from basal diameter and vegetative height, we found
a continuous increase in biomass until June (slope coefficient: $\beta$=
`r b_t`, Fig. \@ref(fig:sbm)c) and that biomass decreaded from June to November (second order effect
of time, $\beta$=`r b_t2`). We did not find evidence that being in patch
changed the sapling biomass ($\beta$=`r b_m`), and this effect was not modulated by
community diversity ($\beta$ = `r b_cm`). We further found weak evidence that
watering decreased the joint effect of patch and diversity on sapling biomass
($\beta$ = `r b_wcm`). We found strong evidence that the biomass of saplings was lower in
diverse communities ($\beta$ = `r b_c`), but it was counteracted by watering
(medium evidence, $\beta$ = `r b_wc`). Watering was found to have a positive
effect on sapling biomass (weak evidence, $\beta$ = `r b_w`). As for survival,
we found variations of the effects of the treatment across species (Fig.
\@ref(fig:sbm)d).

```{r}
tar_load(leaf_inla_effects_scaled)
ldmc_effects <- leaf_inla_effects_scaled %>%
  filter(response == "ldmc")

sla_effects <- leaf_inla_effects_scaled %>%
  filter(response == "sla")

a_m <- get_effect_ci(effect = sla_effects, term = "msPatch", ci_lvl = "0.90")
l_m <- get_effect_ci(effect = ldmc_effects, term = "msPatch", ci_lvl = "0.90", r = 3)

a_cm <- get_effect_ci(effect = sla_effects, term = "comPoly:msPatch", ci_lvl = "0.80")
a_c <- get_effect_ci(effect = sla_effects, term = "comPoly", ci_lvl = "0.95")
a_wc <- get_effect_ci(effect = sla_effects, term = "comPoly:wateringWatered", ci_lvl = "0.90")
a_w <- get_effect_ci(effect = sla_effects, term = "wateringWatered", ci_lvl = "0.80", r = 1)
a_wm <- get_effect_ci(effect = sla_effects, term = "msPatch:wateringWatered", ci_lvl = "0.80")
a_wcm <- get_effect_ci(effect = sla_effects, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
a_dor <- get_effect_ci(effect = sla_effects, term = "speciesdorycnium", ci_lvl = "0.95")
a_pis <- get_effect_ci(effect = sla_effects, term = "speciespistachia", ci_lvl = "0.95")

l_cm <- get_effect_ci(effect = ldmc_effects, term = "comPoly:msPatch", ci_lvl = "0.80")
l_c <- get_effect_ci(effect = ldmc_effects, term = "comPoly", ci_lvl = "0.95")
l_wc <- get_effect_ci(effect = ldmc_effects, term = "comPoly:wateringWatered", ci_lvl = "0.90")
l_w <- get_effect_ci(effect = ldmc_effects, term = "wateringWatered", ci_lvl = "0.95", r = 1)
l_wm <- get_effect_ci(effect = ldmc_effects, term = "msPatch:wateringWatered", ci_lvl = "0.80")
l_wcm <- get_effect_ci(effect = ldmc_effects, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
l_dor <- get_effect_ci(effect = ldmc_effects, term = "speciesdorycnium", ci_lvl = "0.95")
l_pis <- get_effect_ci(effect = ldmc_effects, term = "speciespistachia", ci_lvl = "0.95")
```

```{r, fig.cap = "Leaf traits"}
p_effect_trait <- plot_inla_fixed_effect(leaf_inla_effects_scaled) +
  labs(x = "Standardizing coefficients (beta)", color = "Trait") +
  theme(
    legend.position = "bottom",
    axis.title.y = element_blank()
  )
ggsave(
  filename = "p_effect_trait.pdf",
  plot = p_effect_trait,
  path = here("paper", "graphics"),
  scale = 1.8,
  width = 90,
  height = 90,
  units = "mm",
  dpi = "print"
)
```

```{r}
lt_cap <- paste0("Effects of treatments on Leaf Dry Matter Content (LDMC) and
  Specific Leaf Area (SLA). Slope coefficients are standardized. Points
  represent the mean of the posterior distribution of coefficients; Thin, medium
  and large bars represent the credible interval at 95\\%, 90\\% and 80\\%.") %>%
str_replace_all("\\s+", " ")
```


```{r lt, fig.cap=lt_cap}
knitr::include_graphics(here("paper", "graphics", "p_effect_trait.pdf"))
```

Leaf traits was found to vary across patch and watering treament. We found
moderate evidence that saplings Leaf Dry Matter Content decreased and that
Specific Leaf Area increased in patch (Standardized coefficients: $\beta$' = `r l_m` and `r a_m`
respectively, Fig. \@ref(fig:lt)), meaning that saplings develop a more "resource exploitive"
strategy (or a "resource conservative" strategy) in patches. We further found
strong evidence that LDMC was lower in watered treatment ($\beta$' = `r l_w`)
but not SLA ($\beta$' = `r a_w`). Overall, we did not find evidence that
community diversity affected leaf traits.

## Plant-plant interactions

Using the predictions of the model, we found that the outcome of interactions
between saplings and *Artemisia herba-alba* were driven by interactive effects
between the diversity of sapling communities and the watering treatment (Fig.
\@ref(fig:int)).
We found that competitive interactions dominated in single species communities
non watered for both survival and biomass (Fig.
\@ref(fig:int)a, b). In watered sites, the single species
communities were found to have positive interactions for survival and negative
for biomass. In diverse communities non-watered, we found positive interactions
both in terms survival and biomass, but strongly negative interactions in
watered sites.

Beyond those general effects at the community level, we found strong disparities
using the model at the species level (Fig.
\@ref(fig:int)c, d). In single species communities no watered, we
found that neutral and negative competitive interactions dominated for *A.
citisoides* and *D. pentaphyllum*, but positive interactions for *P. lenticus*
in terms of survival, for all species displayed negative interactions in terms
of biomass. We found strong discrepancies among species in the watered sites,
*A. citisoides* was the most facilitated followed by *D. pentaphyllum* and
competition for *P. lenticus* in term of survival, we found the opposite gradient
in term of biomass, *P. lenticus* being the most facilitated and  *A.
citisoides* displaying the strongest competitive effects. In diverse
communities non watered, we found that *P. lenticus* and *A. citisoides* displayed
strong positive interactions in term of survival while *D. pentaphyllum*
displayed negative interactions, while  *A. citisoides* and *D. pentaphyllum*
displayed positive interactions in terms of biomass but *P. lenticus* displayed
negative interactions. In watered diverse communities, *A. citisoides* and *D.
pentaphyllum* both displayed negative interactions with *A. herba-alba* in terms
of survival and biomass while *P. lenticus* displayed positive in terms of
survival but negative in terms of biomass.


```{r}
tar_load(pp_int_global)
p_int_global_surv <- pp_int_global %>%
  filter(response == c("survival"), species == "anthyllis") %>%
  ggplot(aes(y = inta, x = duration_m + 6, color = com, shape = watering, fill = com), alpha = 1) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 0) +
  geom_ribbon(aes(ymin = inta_low, ymax = inta_high), alpha = .2, color = NA) +
  labs(
    y = "Net interaction (survival)",
    x = "Number of month since the beginning of the experiment") +
  theme_bw()

p_int_global_bm <- pp_int_global %>%
  filter(duration_m == 5,response == "bm", species == "anthyllis") %>%
  ggplot(
    aes(
      y = inta, ymin = inta_low, ymax = inta_high,
      x = com,
      color = com, shape = watering,
      group = watering,
      fill = com
      ),
    alpha = 1, position = "dodge") +
  geom_hline(yintercept = 0) +
  geom_pointrange(position = position_dodge(.5)) +
  labs(
    y = "Net interaction (biomass)",
    x = "Diversity",
    shape = "Watering", color = "Diversity"
    ) +
  theme_bw()

p_int_global <- plot_grid(
  p_int_global_surv + theme(legend.position = "none"),
  p_int_global_bm + theme(legend.position = "none"),
  ncol = 2,
  rel_widths = c(.6, .4),
  labels = c("a", "b")
)
```


```{r}
tar_load(pp_int)
int_surv <- pp_int %>%
  filter(response %in% c("survival"))
p_int_surv <- int_surv  %>%
  ggplot(aes(y = inta, x = duration_m + 6, color = com, shape = watering, fill = com), alpha = 1) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 0) +
  geom_ribbon(aes(ymin = inta_low, ymax = inta_high), alpha = .2, color = NA) +
  facet_grid(cols = vars(species), scales = "free_y") +
  labs(
    y = "Net interaction (survival)",
    x = "Number of month since the beginning of the experiment") +
  theme_bw()

p_int_bm <- pp_int %>%
  filter(duration_m == 5, response == "bm") %>%
  ggplot(
    aes(
      y = inta, ymin = inta_low, ymax = inta_high,
      x = species, color = com, shape = watering,
      group = watering,
      fill = com
      ),
    alpha = 1, position = "dodge") +
  geom_hline(yintercept = 0) +
  geom_pointrange(position = position_dodge(.5)) +
  labs(
    y = "Net interaction (biomass)",
    shape = "Watering", color = "Diversity"
    ) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "bottom"
  )
leg_int <- get_legend(p_int_bm)

p_int_sp <- plot_grid(
  p_int_surv + theme(legend.position = "none"),
  p_int_bm + theme(legend.position = "none"),
  rel_widths = c(.6, .4),
  labels = c("c", "d")
)
```

```{r }
p_int <- plot_grid(
  p_int_global + theme(legend.position = "none"),
  p_int_sp,
  nrow = 2
)
p_int_ok <- plot_grid(
  p_int,
  leg_int,
  rel_heights = c(1, .1),
  nrow = 2
)
ggsave(
  filename = "p_int_ok.pdf",
  plot = p_int_ok,
  path = here("paper", "graphics"),
  scale = 2.4,
  width = 90,
  height = 90 * .6,
  units = "mm",
  dpi = "print"
)
```

```{r}
int_cap <- paste0("Net affects of the interaction sapling-shrub at the community
  (a, b) and at the species level (c, d) for survival (a, c) et biomass (b, d).
  Time is not displayed for biomass because net effect was not found to vary
  across time (Fig. SXX).") %>%
str_replace_all("\\s+", " ")
```


```{r int, fig.cap=int_cap}
knitr::include_graphics(here("paper", "graphics", "p_int_ok.pdf"))
```


# Discussion {-}

Our study aimed to scale plant-plant interactions among saplings and adult plant
at the community level. To do so, we planted sapling communities of three
individuals in open sites or below the canopy of an adult individual of *A.
herba-alba*. We manipulated the diversity and the input of water to the sapling
communities. Using a hierarchical Bayesian model accounting for variation
at the plot and site level, we found that diverse communities had
higher survival and biomass in terms of survival and biomass, an evidence of
strong facilitative effects. We further found that watering downplayed the
positive effect of being under an adult of *A. herba-alba*, resulting in
negative interactions. At the species level, we found strong variations in the
response to watering and diversity in terms of survival and biomass,
suggesting an interplay between stress-tolerance and competitive abilities
of sapling species.

## Diversity, patch and watering {-}

We found that higher diversity of sapling species enhances facilitation at the
community scale. More specifically, only *Pistacia lenticus* displayed a
relatively weak facilitation in single species treatment in term of survival.
This results is accordance with previous studies showing that communities
located under nurse plants tend to have higher species richness
[@cavieres_facilitative_2014]. This result can be explain by the possible
increase in niche complementary (i.e. decrease in niche overlap) among saplings
in diverse communities, which in turn decrease competition for resource
exploitation[@cardinale_species_2002] and increase the
benefits of facilitation [Could it be tested with @loreau_partitioning_2001 ?].

Watering was found to modulate strongly the outcome of the interactions among
saplings and *Artemisia herba-alba*. In monospecific communities, watering
switched the sign of the interactions from negative to relatively weakly
positive for survival. A reason might be that the added water was hold longer
under the canopy of *A. herba-alba*. Possible mechanisms include lower
evapotranspiration under the canopy due to the shading
[@callaway_positive_2007]. Watering was found to increase the overall survival
of sapling and we found weak evidence that watering enhances further the
survival of sapling in *A. herba-alba* patches, which lend toward the hypothesis
of higher watering benefits under *A. herba-alba*. This result seems in
contraction with the Stress Gradient Hypothesis which predicts that improving
local conditions should result in a switch from facilitation to competition
[@bertness_positive_1994]. However, watering was found to drive competition in
diversity-rich sapling communities, i.e. an opposite effect from monospecific
communities. More specifically, we found that watering treatment had more
positive effects on survival and biomass in diverse communities while watering
was decreasing the positive effect of being in a patch and in diverse
communities. Hence, watering seems to make that diverse sapling communities
experiment more competition than facilitation from *A. herba-alba*. This result
is in line with the Stress-Gradient-Hypothesis that propose that positive
interactions should predominate in more benign environment
[@bertness_positive_1994]. Interestingly, it was not the case in single species
communities which suggests that biotic stress, here intraspecific interactions
among saplings, play an important role in driving the outcome of interactions
between saplings and *A. herba-alba*.

```{r}
idea_cap <- paste0("Including both abiotic stress and among beneficiary
  competition in the Stress Gradient hypothesis. (a) Both low/high competition
  among beneficiary species and abiotic stress result in a negative net effect
  between beneficiary and benefactors (1, 4). Positive net effects are more
  likely to arise if either competition among beneficiary is decreased by
  increasing diversity (2) or if abiotic stress is decreased (3). (b) Both the
  effects of abiotic stress and the level of competition among benefiaries can
  be map in the original SGH framework (Bertness \\& Callaway, 1994)") %>%
  str_replace_all("\\s+", " ")
```


```{r idea, fig.cap=idea_cap}
knitr::include_graphics(here("paper", "competition_stress_sgh.pdf"))
```


The consideration of both abiotic stress and competition among saplings might
then be the key to understand observed outcome sapling-shrub interactions (Fig.
\@ref(fig:idea)).
Previous studies showed that biotic stressors such as grazing can lead to the
pattern of SGH alike abiotic stressors[@smit_inclusion_2009;
@graff_testing_2011; @verwijmeren_interspecific_2013;
@verwijmeren_drought_2014]. Further conceptual development highlighted that
multiple stressors can drive plant-plant interactions, such as resource (e.g.
water) or non resource (e.g. temperature, wind) and biotic stressors (e.g.
grazing) [@maestre_refining_2009; @graff_species_2017]. However, a missing link
is the consideration of competition between the plants that benefit from the
nurse plant, which can be considered as another type of biotic stress. We then
propose a framework including both interactions among the beneficiary plants and
the level of abiotic stress (Fig. \@ref(fig:idea)a). Competition between sapling
community and adult shrub should dominate when both abiotic stress and
competition among saplings is strong are high or low. Then, facilitation between
sapling community and adult shrub are expect to arise when either by decreasing
abiotic stress (e.g. by watering in our experiment, Fig. \@ref(fig:idea)a from 4
to 3) or by decreasing competition inside the beneficiary community (e.g. by
increasing diversity in our experiment, Fig. \@ref(fig:idea)a from 4 to 2). We
can then map both abiotic stress and competition among saplings on a single
gradient dimension to explain how the joint effects of watering and community
diversity can affect the outcome of sapling-shrub interactions in the original
framework of the SGH (Fig. \@ref(fig:idea)b) [@bertness_positive_1994;
@maestre_refining_2009]. As understory communities were reported to be composed
of numerous species [@cavieres_facilitative_2014], the consideration of the
competition inside understory communities might help us to understand the
mechanisms driving the assembly of understory communities in natural
communities.

We further found species variations in their response to the treatments. (Give
some example). However, we did not find evidence of a relationship between
stress-tolerance of the species and the outcome of sapling-shrub interactions
[@graff_species_2017; @liancourt_stress_2005]. According to this hypothesis, *P.
lenticus*, *D. pentaphyllum* and *A. citisoides*, that had lower to the highest
survival in the open sites, should have respectively experiment the highest from
the lower facilitation in single species treatment. In turn, we found that *P.
lenticus*, *D. pentaphyllum* and *A. citisoides* respectively had a balance of
interaction respectively positive, negative and neutral with *A. herba-alba* in
single species treament. Hence, this hypothesis hold by considering *P.
lenticus* and *A. anthyllus*, the two species at the extrem of the
Competitive/Stress-tolerance spectrum, but not if we consider *D. pentaphyllum*.
It might be explained by the intraspecific competition among *D. pentaphyllum*
but also that the phytoxicity of *A. herba-alba*. *A. herba-alba* was reported
to produce strong anti-germination coumpounds but was not reported affect
negatively sapling growth [@arroyo_phytotoxic_2018].

In line with previous studies, we found that watering and patch leaded to
similar changes in functional traits, driving higher SLA and lower LDMC. More
specifically, we found that LDMC decreased in watered sites and in patch sites.
This indicates that watered and plants located under *A. herba-alba* devolped a
less resource-conservative strategy and a more resource acquisition strategy.
However, we found an increase in SLA in the patch treatment but not in the
watering treatment. Light limitation and water deficit might explain this
pattern[@liu_does_2016]. Previous studies showed that light reduction results
in higher SLA, which is a compensation for the limited amount of radiation
received and a common adaptation for understory plants[@liu_does_2016].
Another hypothesis is that the decrease in SLA overall under *A. herba-alba* is
not happening in watering treatment because of the water deficit in open sites
which in turn might promote to the maintenance of the same leaf area despite the
increase of water input.


# Conclusion & perspectives


# References
