---
title: "Supplementary Figures"
author: "Alain Danet, Susana Bautista, ..., Fabien Anthelme, Sonia Kéfi"
date: ""
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
  officedown::rdocx_document:
bibliography: "bibliography.bib"
csl: "nature.csl"
link-citations: true
toc: false
linestretch: 2.0
---


```{r}
tar_load(c(inla_surv_sp_effects, inla_surv_sp_odd))

s_t <- get_effect_ci(effect = inla_surv_sp_odd, term = "duration_m", ci_lvl =
  "0.95", p = FALSE, r = 2)

s_dor <- get_effect_ci(effect = inla_surv_sp_odd, term = "speciesdorycnium",
  ci_lvl = "0.95")
s_pis <- get_effect_ci(effect = inla_surv_sp_odd, term =
  "speciespistachia", ci_lvl = "0.95")

s_ca <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly", ci_lvl = "0.95", p = FALSE, r = 2)
s_cd <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:speciesdorycnium", ci_lvl = "0.95", p = FALSE, r = 2)
s_cp <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:speciespistachia", ci_lvl = "0.95", r = 0)

s_ma <- get_effect_ci(effect = inla_surv_sp_odd, term = "msPatch", ci_lvl = "0.80")
s_md <- get_effect_ci(effect = inla_surv_sp_odd, term = "msPatch:speciesdorycnium", ci_lvl = "0.80")
s_mp <- get_effect_ci(effect = inla_surv_sp_odd, term = "msPatch:speciespistachia", ci_lvl = "0.80")

s_cma <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:msPatch", ci_lvl = "0.90")
s_cmd <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:msPatch:speciesdorycnium", ci_lvl = "0.80")
s_cmp <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:msPatch:speciespistachia", ci_lvl = "0.80")

s_wa <- get_effect_ci(effect = inla_surv_sp_odd, term = "wateringWatered", ci_lvl = "0.95")
s_wd <- get_effect_ci(effect = inla_surv_sp_odd, term = "wateringWatered:speciesdorycnium", ci_lvl = "0.80")
s_wp <- get_effect_ci(effect = inla_surv_sp_odd, term = "wateringWatered:speciespistachia", ci_lvl = "0.95")

s_wma <- get_effect_ci(effect = inla_surv_sp_odd, term = "msPatch:wateringWatered", ci_lvl = "0.80")
s_wmd <- get_effect_ci(effect = inla_surv_sp_odd, term = "msPatch:wateringWatered:speciesdorycnium", ci_lvl = "0.80")
s_wmp <- get_effect_ci(effect = inla_surv_sp_odd, term = "msPatch:wateringWatered:speciespistachia", ci_lvl = "0.80")

s_wca <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:wateringWatered", ci_lvl = "0.95")
s_wcd <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:wateringWatered:speciesdorycnium", ci_lvl = "0.95")
s_wcp <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:wateringWatered:speciespistachia", ci_lvl = "0.95")

s_wcma <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
s_wcmd <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:msPatch:wateringWatered:speciesdorycnium", ci_lvl = "0.80")
s_wcmp <- get_effect_ci(effect = inla_surv_sp_odd, term = "comPoly:msPatch:wateringWatered:speciespistachia", ci_lvl = "0.80")
unique(inla_surv_perc$term)
```

```{r}
plot_inla_fixed_effect(inla_surv_odd, color_var = NULL, intercept = 1) +
  labs(x = "Change in survival likelihood (%)") +
  theme(axis.title.y = element_blank())
```

```{r}
tar_load(c(inla_surv_effects, inla_surv_odd))

s_t <- get_effect_ci(effect = inla_surv_odd, term = "duration_m", ci_lvl =
  "0.95", p = FALSE, r = 2)

s_dor <- get_effect_ci(effect = inla_surv_odd, term = "speciesdorycnium",
  ci_lvl = "0.95")
s_pis <- get_effect_ci(effect = inla_surv_odd, term =
  "speciespistachia", ci_lvl = "0.95")

s_ca <- get_effect_ci(effect = inla_surv_odd, term = "comPoly", ci_lvl = "0.95", p = FALSE, r = 2)
s_cd <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:speciesdorycnium", ci_lvl = "0.95", p = FALSE, r = 2)
s_cp <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:speciespistachia", ci_lvl = "0.95", r = 0)

s_ma <- get_effect_ci(effect = inla_surv_odd, term = "msPatch", ci_lvl = "0.80")
s_md <- get_effect_ci(effect = inla_surv_odd, term = "msPatch:speciesdorycnium", ci_lvl = "0.80")
s_mp <- get_effect_ci(effect = inla_surv_odd, term = "msPatch:speciespistachia", ci_lvl = "0.80")

s_cma <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch", ci_lvl = "0.90")
s_cmd <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch:speciesdorycnium", ci_lvl = "0.80")
s_cmp <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch:speciespistachia", ci_lvl = "0.80")

s_wa <- get_effect_ci(effect = inla_surv_odd, term = "wateringWatered", ci_lvl = "0.95")
s_wd <- get_effect_ci(effect = inla_surv_odd, term = "wateringWatered:speciesdorycnium", ci_lvl = "0.80")
s_wp <- get_effect_ci(effect = inla_surv_odd, term = "wateringWatered:speciespistachia", ci_lvl = "0.95")

s_wma <- get_effect_ci(effect = inla_surv_odd, term = "msPatch:wateringWatered", ci_lvl = "0.80")
s_wmd <- get_effect_ci(effect = inla_surv_odd, term = "msPatch:wateringWatered:speciesdorycnium", ci_lvl = "0.80")
s_wmp <- get_effect_ci(effect = inla_surv_odd, term = "msPatch:wateringWatered:speciespistachia", ci_lvl = "0.80")

s_wca <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:wateringWatered", ci_lvl = "0.95")
s_wcd <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:wateringWatered:speciesdorycnium", ci_lvl = "0.95")
s_wcp <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:wateringWatered:speciespistachia", ci_lvl = "0.95")

s_wcma <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
s_wcmd <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch:wateringWatered:speciesdorycnium", ci_lvl = "0.80")
s_wcmp <- get_effect_ci(effect = inla_surv_odd, term = "comPoly:msPatch:wateringWatered:speciespistachia", ci_lvl = "0.80")
unique(inla_surv_perc$term)
```

---
#We found strong evidence that time decreased odd of survival (Odd-Ratio = `r s_t`).
#We further found strong evidence that *Pistachia lentiscus* and
#*Dorycnium pentaphyllum* saplings had a lower survival likelihood than
#*Anthyllis citisoides* (respectively OR = `r s_pis`, OR: `r s_dor`).
#We found strong evidence that diverse communities decreased the odd of survival
#of *A. citisoides* (OR = `r s_ca`), but increase the odds of survival of
#*D. pentaphyllum* and *P. lentiscus* (resp. OR: `r s_cd` and `r s_cp`).
#Surpringly, we did not evidence of an overall effect of being in a patch of *A.
#herba-alba* on the odd of survivals of the sapling species (OR = `r s_ma`,
#`s_md`, `s_mp`, for *A. citisoides*, *D. pentaphyllum*, and *P. lentiscus*
#resp.), but we found moderate evidence that *A. herba-alba* had an higher
#positive effect on odds of survival in diverse communities (OR = `r s_cma`),
#independently of species identity (OR = `r s_cmd` and `r s_cmp`). Finally,
#the watering treatment decreased the positive effect of *A. herba-alba* in diverse
#communities for *A. citisoides* (strong evidence, OR = `r s_wcma`), but enhanced
#it for *D. pentaphyllum* and *P. lentiscus* (weak evidence, OR = `r s_wcmd` and
#`r s_wcmp` resp.).
#
#We found strong evidence that the watering treatment increased the odds of
#survival in the open sites for *A. citisoides*, and *P. lentiscus*
#(OR = `r s_wa`, `r s_wd` resp.), but did not affect *D. pentaphyllum*
#(OR = `r s_wp`). The effect of being in a patch of *A. herba-alba* was not affected
#by watering (OR = `r s_wma` and `r s_wmd` for *A. citisoides* and *D.
#pentaphyllum*) but decreased the odds of survival for *P. lentiscus* (weak
#evidence, OR = `r s_wmp`). We futher found strong evidence that watering
#increased even more the odd of survival in *A. citisoides* (OR = `r s_wca`) in
#diverse communities, but decreased it for *D. pentaphyllum* and *P. lentiscus*
#(OR = `r s_wcd`, `r s_wcp` resp.).
---

```{r}
plot_inla_fixed_effect(bm_inla_scaled_effects,
  color_var = response, intercept = 0) +
  labs(x = "Change in survival likelihood (%)") +
  theme(axis.title.y = element_blank())
```

```{r}
ldmc_scaled_effects <- leaf_inla_sp_scaled_effects %>%
  filter(response == "ldmc")
l_t <- get_effect_ci(effect = ldmc_scaled_effects, term = "duration_m", ci_lvl =
  "0.95", p = FALSE, r = 2)
l_dor <- get_effect_ci(effect = ldmc_scaled_effects, term = "speciesdorycnium",
  ci_lvl = "0.95")
l_pis <- get_effect_ci(effect = ldmc_scaled_effects, term =
  "speciespistachia", ci_lvl = "0.95")
l_ca <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly", ci_lvl = "0.95", p = FALSE, r = 2)
l_cd <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:speciesdorycnium", ci_lvl = "0.95", p = FALSE, r = 2)
l_cp <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:speciespistachia", ci_lvl = "0.95", r = 0)
l_ma <- get_effect_ci(effect = ldmc_scaled_effects, term = "msPatch", ci_lvl = "0.80")
l_md <- get_effect_ci(effect = ldmc_scaled_effects, term = "msPatch:speciesdorycnium", ci_lvl = "0.80")
l_mp <- get_effect_ci(effect = ldmc_scaled_effects, term = "msPatch:speciespistachia", ci_lvl = "0.80")
l_cma <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:msPatch", ci_lvl = "0.90")
l_cmd <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:msPatch:speciesdorycnium", ci_lvl = "0.80")
l_cmp <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:msPatch:speciespistachia", ci_lvl = "0.80")
l_wa <- get_effect_ci(effect = ldmc_scaled_effects, term = "wateringWatered", ci_lvl = "0.95")
l_wd <- get_effect_ci(effect = ldmc_scaled_effects, term = "wateringWatered:speciesdorycnium", ci_lvl = "0.80")
l_wp <- get_effect_ci(effect = ldmc_scaled_effects, term = "wateringWatered:speciespistachia", ci_lvl = "0.95")
l_wma <- get_effect_ci(effect = ldmc_scaled_effects, term = "msPatch:wateringWatered", ci_lvl = "0.80")
l_wmd <- get_effect_ci(effect = ldmc_scaled_effects, term = "msPatch:wateringWatered:speciesdorycnium", ci_lvl = "0.80")
l_wmp <- get_effect_ci(effect = ldmc_scaled_effects, term = "msPatch:wateringWatered:speciespistachia", ci_lvl = "0.80")
l_wca <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:wateringWatered", ci_lvl = "0.95")
l_wcd <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:wateringWatered:speciesdorycnium", ci_lvl = "0.95")
l_wcp <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:wateringWatered:speciespistachia", ci_lvl = "0.95")
l_wcma <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:msPatch:wateringWatered", ci_lvl = "0.95")
l_wcmd <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:msPatch:wateringWatered:speciesdorycnium", ci_lvl = "0.80")
l_wcmp <- get_effect_ci(effect = ldmc_scaled_effects, term = "comPoly:msPatch:wateringWatered:speciespistachia", ci_lvl = "0.80")
```
Leaf traits were found to vary across treatments, traits, and species.
*Pistachia lentiscus* and *Dorycnium pentaphyllum* had overall and higher LDMC
and lower SLA than *Anthyllis citisoides* (strong evidence). We did not find
evidence for an overall effect of community diversity for leat trait in any species ().

```{r, eval = FALSE}
tar_load(c(leaf_trait, leaf_inla_sp_scaled_effects))
plot_inla_fixed_effect(leaf_inla_sp_scaled_effects)

leaf_species <- plot_inla_fixed_effect(
  leaf_inla_sp_scaled_effects %>%
    filter(str_detect(term, "dorycnium|pistachia")), #, response %in% c("d", "h")
  color_var = response) +
  labs(x = "Change in survival likelihood (%)")
leaf_base <- plot_inla_fixed_effect(leaf_inla_sp_scaled_effects %>%
    filter(!str_detect(term, "dorycnium|pistachia")), #, response %in% c("d", "h")
  color_var = response) +
  labs(x = "Change in survival likelihood (%)")

plot_grid(leaf_base, leaf_species)

leaf_trait %>%
  group_by(ms, com, watering, species, plot) %>%
  summarise(ldmc = mean(ldmc)) %>%
  ggplot(aes(y = ldmc, x = species, color = ms, shape = com, alpha = .5)) +
  geom_jitter() +
  #geom_line(data = inla_surv_sp_pred, aes(y = mean, linetype = com)) +
  facet_grid(rows = vars(watering)) +
  theme_bw()

surv_data_modelling %>%
  group_by(duration_m, ms, com, watering, species, plot) %>%
  summarise(survival = sum(survival) / n()) %>%
  ggplot(aes(y = survival, x = duration_m + 6, color = ms, shape = com, alpha = .5)) +
  geom_jitter() +
  geom_line(data = inla_surv_pred, aes(y = mean, linetype = com)) +
  facet_grid(cols = vars(species), rows = vars(watering)) +
  theme_bw()
```

```{r}
tar_load(bm_inla_sp_scaled_effects)

bm_species <- plot_inla_fixed_effect(
  bm_inla_sp_scaled_effects %>%
    filter(str_detect(term, "dorycnium|pistachia")), #, response %in% c("d", "h")
  color_var = response) +
  labs(x = "Change in survival likelihood (%)")
bm_base <- plot_inla_fixed_effect(bm_inla_sp_scaled_effects %>%
    filter(!str_detect(term, "dorycnium|pistachia")), #, response %in% c("d", "h")
  color_var = response) +
  labs(x = "Change in survival likelihood (%)")

plot_grid(bm_base, bm_species)
```

```{r, eval=FALSE}
tar_load(inla_surv_sp_perc)
surv_species <- plot_inla_fixed_effect(
  inla_surv_sp_perc %>%
    filter(str_detect(term, "dorycnium|pistachia")),
  color_var = NULL) +
  labs(x = "Change in survival likelihood (%)") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y.right = element_blank(),
    axis.ticks.y.right = element_blank()
    ) +
  scale_x_break(c(1500, 8000))
surv_base <- plot_inla_fixed_effect(inla_surv_sp_perc %>%
    filter(!str_detect(term, "dorycnium|pistachia")),
  color_var = NULL) +
  labs(x = "Change in survival likelihood (%)") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y.right = element_blank(),
    axis.ticks.y.right = element_blank()
    ) +
  scale_x_break(c(1500, 3000))

plot_grid(print(surv_base), print(surv_species))
```

```{r, eval=TRUE}
tar_load(c(surv_data, surv_data_modelling, inla_surv_pred))
tar_load(inla_surv_sp_pred)
tar_load(surv_raw_data)

surv_raw_data %>%
  pivot_longer(cols = c(h, d, hm), names_to = "variable", values_to = "values") %>%
  group_by(month, variable) %>%
  summarise(n_na = sum(is.na(values))) %>%
  ggplot(aes(x = month, y = n_na)) +
  geom_line() +
  facet_grid(cols = vars(variable))

surv_data_modelling %>%
  group_by(duration_m, ms, com, watering, species, plot) %>%
  summarise(survival = sum(survival) / n()) %>%
  ggplot(aes(y = survival, x = duration_m + 6, color = ms, shape = com, alpha = .5)) +
  geom_jitter() +
  geom_line(data = inla_surv_sp_pred, aes(y = mean, linetype = com)) +
  facet_grid(cols = vars(species), rows = vars(watering)) +
  theme_bw()

surv_data_modelling %>%
  group_by(duration_m, ms, com, watering, species, plot) %>%
  summarise(survival = sum(survival) / n()) %>%
  ggplot(aes(y = survival, x = duration_m + 6, color = ms, shape = com, alpha = .5)) +
  geom_jitter() +
  geom_line(data = inla_surv_pred, aes(y = mean, linetype = com)) +
  facet_grid(cols = vars(species), rows = vars(watering)) +
  theme_bw()
```

```{r}
tar_load(c(bm_inla_pred, bm_inla_sp_pred))
surv_data_modelling %>%
  group_by(duration_m, ms, com, watering, species, plot) %>%
  summarise(d = mean(d, na.rm = TRUE)) %>%
  ggplot(aes(y = d, x = duration_m + 6, color = ms, shape = com, alpha = .5)) +
  geom_jitter() +
  geom_line(data = bm_inla_sp_pred %>% filter(response == "d"), aes(y = mean, linetype = com)) +
  facet_grid(cols = vars(species), rows = vars(watering)) +
  theme_bw()

surv_data_modelling %>%
  group_by(duration_m, ms, com, watering, species, plot) %>%
  summarise(h = mean(h, na.rm = TRUE)) %>%
  ggplot(aes(y = h, x = duration_m + 6, color = ms, shape = com, alpha = .5)) +
  geom_jitter() +
  geom_line(data = bm_inla_sp_pred %>% filter(response == "h"), aes(y = mean, linetype = com)) +
  facet_grid(cols = vars(species), rows = vars(watering)) +
  theme_bw()

surv_data_modelling %>%
  group_by(duration_m, ms, com, watering, species, plot) %>%
  summarise(bm = mean(bm, na.rm = TRUE)) %>%
  ggplot(aes(y = bm, x = duration_m + 6, color = ms, shape = com, alpha = .5)) +
  geom_jitter() +
  geom_line(data = bm_inla_sp_pred %>% filter(response == "bm"), aes(y = mean, linetype = com)) +
  facet_grid(cols = vars(species), rows = vars(watering)) +
  theme_bw()
```

```{r}
int_tot %>%
  select(response, duration_m, com, watering, species, response, inta) %>%
  pivot_wider(names_from = "response", values_from = "inta") %>%
  ggplot(aes(y = survival, x = duration_m, color = com, shape = watering)) +
  geom_line() +
  facet_grid(cols = vars(species)) +
  theme_bw()
```

